### 2023-01-27 text/ManuscriptDraft.Rmd
Added data to gitignore because of large tiffs

---
new_session: FALSE
#title: |
#  **Detecting small objects and many of them: Using computer vision and deep learning to automate counting of collembola in petri dish samples**
#date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
  html_document:
    df_print: paged
fontfamily: mathpazo
fontsize: 12pt
geometry: margin = 1in
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{dcolumn}
- \usepackage{caption}
- \usepackage{float}
- \usepackage{afterpage}
- \usepackage{siunitx}
- \usepackage{amsmath}
#keywords: X
bibliography: ./library.bib
csl: ./journal-of-ecology.csl
---

```{r eval = FALSE, echo=FALSE}
library(knitr)
knit('ManuscriptDraft.Rmd')
rmarkdown::render("ManuscriptDraft.Rmd", output_file = "ManuscriptDraft.docx")
system2("open","manuscriptDraft.docx")
```

```{r echo=FALSE}
# Function for creating word comments in Rmarkdown
# Use: This text contains a `r word_comment("This is the comment", "comment.")`.

word_comment <- function(comment, highlight = "") {
  if (isTRUE(knitr:::pandoc_to() == "docx")) {
    paste0('[', comment, ']{.comment-start id="0" author="Hjalte M."',
           'date="2020-01"}', highlight, '[]{.comment-end id="0"}')
  }
}
```

Title:

**Detecting small objects and many of them: Using computer vision and deep learning to automate counting of collembola in petri dish samples**

#

Authors:

Hjalte M. R. Mann^1^, James J. Scott-Fordsmand^1^, Toke T. Høye^1^

#

Author affiliations:

1: Department of Ecoscience, Aarhus University, C.F. Møllers Allé 4-8, 8000 Aarhus C, Denmark\

#

Corresponding author contact information:

Hjalte Mads Rosenstand Mann\
E-mail: [mann\@ecos.au.dk](mailto:mann@ecos.au.dk){.email}\
Phone: +45 31178585

#

ORCID IDs:

HMRM: 0000-0002-4768-4767, JJSF: 0000-0002-2260-1224, TTH: 0000-0001-5387-3284

#

Keywords: Collembola, computer vision, deep learning

#

Article type: Research article

Word count: 0

\newpage

# Abstract

Here's the abstract.

\newpage

# Introduction

-Why do we need to count collembola in petri dishes
-What is the problem with the established method
-Developments in computer vision
-How can computer vision help solve our problem
-What are we presenting

Counting of collembola in petri dish samples in ecotoxicology experiments requires substantial manual labor by trained technicians. The process is time-consuming while the result is a simple census of the present individual collembola. Here, we investigated the feasibility of automating collembola counting based on a single image of a sample taken with a handheld camera and a deep learning object detection model.

Object detection models have gained significant attention for their ability to locate specific objects of interests in images. However, reliable detection of very small and very large numbers of objects remains a challenging task. In this regard, the present task is particularly challenging owing to the very small size of objects, low distinguishability of animals from background noise, large variation in number of objects in an image, visual variation between samples, and variation in the conditions in which the image was taken, how the image was taken and the camera that was used.

In order to ease the manual counting of animals in an image, it is often done by taking an image of the sample and performing the counting in image processing software. This allows for marking of counted individual to prevent double-counting and missed individuals and validation of result.

One approach has been semi-automated background removal to create a binary blob image ideally containing only animals and all the animals in a dish. This has allowed for subsequent automated counting of blobs and thus individuals. However, this process still requires substantial manual effort to clean the image and separate individuals to produce reliable results.

Ideally, counting would be entirely automated with just a single RGB image as input.

The basis of this was the output of manual processing of images

We publish the code together with the trained model to facilitate others to implement automated analysis of ecotoxicology samples.

# Material and methods

-	Overview of method
o	Standard method
o	Translating binary to bounding box format for model training
o	Splitting image/annotation data into training, validation, and testing sets
o	Slicing images/annotations for full resolution training
o	Training and testing neural network with sliding window approach

The method involved several steps: Translating binary filter images to bounding box format; splitting images into training, validation and testing sets; slicing images and associated annotations to a standard size in order to not loose information from large images because of downscaling; training and testing the neural network with a sliding window approach.

## Generating training and testing data

Images had substantial variation in size, with the smallest image included being XxX and the largest XxX. We sliced to 640 x 640. Images were only sliced on dimensions larger than 640, i.e., an image with size 100x1280 would be sliced to two image of 100x640.

Training and testing object detection models requires annotated training and testing data. Specifically, images containing the objects of interest together with associated annotation data containing coordinates for bounding boxes delimiting the objects are required. Here, generation of annotation data was done through automated processing of existing outputs from human analysis. The human analysis results in a binary mask output of each petri dish image with black blobs delimiting animals. To convert these to bounding boxes, we applied automated contour detection and bounding box creation using Python OpenCV. The contour detection produces some errors when there are many objects very close to each other. Although the error rate seems low, for this test, images with a very high number of objects were discarded. Images from four tests were used (Test A-D). Only one image of each sample was used (i.e. for A1.1, A1.2, etc., only one image was included).

Contour detection and bounding box derivation was performed for a total of 127 images resulting in a total of 110.553 objects detected and annotated. See table x for distribution of images and objects between groups.

Group	Images	Objects
A	44	66056
B	39	17479
C	16	17059
D	28	9959

To decrease risk of objects not contained in bounding box, we expanded the widths and heights of boxes with 10%.

## Splitting data into training, validation, and testing

The images varied substantially in the number of annotated objects they contained. For each experimental group, we split the images into training, validation, and testing at a ratio of 70/15/15 at the level of images while optimizing for a ratio of 70/15/15 at the level of objects. If 70% of the images resulted in an unequal remainder or a decimal value, we rounded to a number that would ensure an equal remainder. This was done so that we could ensure an equal split between validation and testing in terms of number of images. We assigned images to groups by treating the problem as a linear programming problem with the number of images assigned to each group constrained to the 70/15/15 split while the distribution of images to groups were optimized towards lowest deviation from the 70/15/15 split at the level of objects assigned to each group.

## Slicing images and annotations

As the suggested method will produce overlap between sliced images when full 640x640 slices cannot be produced, individual animals will sometimes be present in more than one slice.

Slicing produced the following distribution of sliced images and objects:

Set         Images    Objects
Training    
Validation    
Testing

TO DO	# images	# objects
Train	89	
Val	19	
Test	19	
Total	127

## Training and testing neural network with sliding window approach
Just do the slice+SAHI approach and compare with standard 640x640.

Deep learning methods
To test the applicability of object detection models for automatic detection and counting of collembola, we tested two model sizes of the object detection architecture YOLOv5: the small YOLOv5s which takes images with dimensions of 640x640 as input (hereafter referred to as YOLOv5 640), and the YOLOv5s6 which takes images of dimensions 1280x1280 (hereafter referred to as YOLOv5 1280).
Additionally, we tested the applicability of the Slicing Aided Hyper Inference (SAHI) method for each model. This method slices each image during inference in a sliding window manner and performs inference on each slice. The method is particularly relevant for detection of small objects.
Training length was set to 1000 epochs with early stopping with a patience of 100 epochs. Confidence threshold for prediction set to 0.1. Non-maximum suppression IOU threshold set to 0.45.

Evaluating detection performance
Since YOLOv5+SAHI has a different output format than YOLOv5 on its own, customs scripts were created to 1) translate YOLOv5 output pickle files to standard YOLOv5 text files and 2) calculate detection performance variables (precision and recall) for both methods. Precision is the number of correct predictions out of all predictions made. Recall is the proportion of the true number of objects that were detected by the model. F1 is the weighted average of precision and recall. A value of 0.3 was used as the IOU threshold for whether bounding boxes overlapped sufficiently to be considered correct.

# Results

-	Overview of original number of images, lowest resolution, highest resolution, 
-	Translating binary filters to bounding box format
o	lowest number of annotations, highest number of annotations
-	Splitting images+annotations into training, validation, testing, with linear optimization (at image level but on condition of number of annotations in each set)
-	Slicing images and annotations to avoid downscaling leverage full resolution information
o	Resulting number of images (mean number of annotations, sd?)
-	Training and testing model
o	Prediction accuracy

The model trained on the 640x640 pixel images reached best validation accuracy at epoch 505. The model trained on the 1280x1280 pixel images reached best validation accuracy at epoch 705.
Table 1 Detection accuracy with the different models.
Method (IOU 0.3)	Precision	Recall	F1
YOLOv5 640	0.46	0.19	0.27
YOLOv5 640 + SAHI (128)	0.60	0.12	0.20
YOLOv5 1280	0.54	 0.56	0.55
YOLOv5 1280 + SAHI (128)	0.63	0.41	0.50

Table 2 Detection accuracy of YOLOv5 1280 + SAHI with different window sizes for the SAHI slicing (256, 128, 64).
Model 1280	SAHI 256	SAHI 128	SAHI 64
IOU 0.3	Precision	Recall	Precision	Recall	Precision	Recall
	0.57	0.47	0.63	0.41	0.66	0.41

Fig. 1 Example of image with challenging background. Result from model 640 + SAHI 128. For this image, the precision was 0.16 and the recall 0.83.

Fig. 2 Example image from test data set. Green bounding boxes are ground truth annotations derived from the binary images. Red boxes are detections made by the YOLOV5 1280 model + SAHI. In this case, most animals marked in the ground truth are detected by the model (high recall), but the model produces many false positives (low precision). Note the overlapping detections in one place (middle of image).

Fig. 3 Example outputs from the two different model sizes with and without application of SAHI (128x128 window size). P: precision, r: recall.

Table 3 Variation in performance between images (YOLOv5 1280 + SAHI 128).
Image	Precision	Recall
A11.1	0.78	1.0
A17.1	0.54	0.79
A31.1	0.42	0.71
A38.1	0.73	0.50
A49.1	0.10	1.0
A6.1	0.60	0.78
B37.1	0.53	0.39
C3.1	0.48	0.85
C7.3	0.62	0.68
D23.1	0.82	0.44
D4.1	0.20	0.20
D9.1	0.66	0.09

# Discussion

-	What did we present
-	Who can use it – and how
o	Model ready to test
o	Code available for training on new data and adaption
-	High resolution images taken in a standardized setting for training and production likely to improve results and should be considered in future studies.
-

The improved precision with increased image dimensions and with the application of SAHI underlines that a main challenge of the task of detecting collembola is the very small object sizes relative to the full image.

Overlapping detections
The models tended to produce overlapping detections. This will have some influence on the accuracy metrics, but it can be assumed to be minor, since the overlapping detections seems to be rare. Overlapping detections are usually removed by non-maximum suppression. However, for the present case with very small object, the NMS IOU threshold was likely set too high,

Accuracy of the ground truth annotations
Considering the similarity between background and animals, there is likely some level of error in the annotations. On top of this, the automated extraction of bounding boxes from the binary images could introduce error, e.g. when there are many objects close to each other (all though in the present case, such images were discarded). If the accuracy of these ground truth annotations is in fact low, it will have detrimental effects on model accuracy. To investigate this issue it could be relevant to test the variation in manual annotations between annotators.

Variation in accuracy between test images
The model accuracy generally varied substantially between images within the test set. This is likely because the model has not been trained on a training set of sufficient size and variation, which means the models fails to generalize between images.

Different issues with data means that the present experiment was carried out on a limited set of images.
Issues/challenges with the available data
-	Contour errors when objects are many and close.
-	Test E folder contains no original images (only b/w), so these cannot be used.
-	Many original images without associated b/w image.
-	Several versions of some b/w images. Used latest version in each case.
-	Images have varied dimensions. Standardized by padding as described. This also means variation in size of objects (in pixels).

# Acknowledgements

xxx

# Author contributions

HRMR, JJSF and TTH conceived the idea. HMRM conceived and developed the method with contributions from JJSF and TTH. HMRM wrote all code. HMRM wrote the manuscript with contributions from JJSF and JJSF. All authors gave final approval for publication.

# Data availability

The code and data that supports the results in this paper is openly available at <https://github.com/TECOLOGYxyz/springtail>.

\newpage

# References

### 2023-01-27 code/analysis.py

@@ -1,0 +1,166 @@
+import motmetrics as mm
+import pandas as pd
+import os
+
+# """
+# SAHI outputs predictions in .pickle files. Below we convert these to text files in yolov5 format.
+# """
+
+# pathPickles = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\smallExp1280\results\1280_e705_s256\pickles'
+# pickles = [os.path.join(pathPickles, i) for i in os.listdir(pathPickles)]
+# factor = 1280
+
+# for p in pickles:
+#     pick = pd.read_pickle(p)
+#     print(p)
+#     pb = os.path.splitext(p)[0]
+#     print(pb)
+#     with open(os.path.join(pb + ".txt"), 'w') as f:
+#         for o in pick:
+#             l = vars(vars(o)['bbox'])
+#             print(l)
+
+#             xmin = l['minx']
+#             ymin = l['miny']
+#             xmax = l['maxx']
+#             ymax = l['maxy']
+
+#             c = 0
+#             xc = ((xmin + xmax)/2)/factor
+#             yc = ((ymin + ymax)/2)/factor
+#             w = (xmax - xmin)/factor
+#             h = (ymax - ymin)/factor
+            
+#             f.write(f'{c} {xc} {yc} {w} {h}\n')
+            
+
+########################################
+
+from shapely.geometry import Polygon
+import numpy as np
+import os
+import csv
+
+
+
+def yolo_to_poly(box):
+    #YOLOv5 annotations are xc, yc, w, h (standardized to image dimensions)
+    #Shapely iou calculation takes tl, tr, bl, br.
+
+
+    #xc, yc, w, h = int(box[1]*factor), int(box[2]*factor), int(box[3]*factor), int(box[4]*factor)
+    xc, yc, w, h = box[1], box[2], box[3], box[4]
+
+    tl = [(xc-(w/2)), (yc-(h/2))]
+    tr = [(xc+(w/2)), (yc-(h/2))]
+    bl = [(xc-(w/2)), (yc+(h/2))]
+    br = [(xc+(w/2)), (yc+(h/2))]
+    
+    # tl = [int(box[1]*factor-(box[3]*factor/2)), int(box[2]*factor-(box[4]*factor/2))]
+    # tr = [int(box[1]*factor+(box[3]*factor/2)), int(box[2]*factor+(box[4]*factor/2))]
+    # bl = [int(box[1]*factor-(box[3]*factor/2)), int(box[2]*factor+(box[4]*factor/2))]
[…]

### 2023-01-27 code/copier.py

@@ -1,0 +1,16 @@
+import shutil
+import os
+
+namePath = r'O:\Tech_TTH-BITCue\Workspace_Hjalte\candida\3rd sending - photos F. candida tes ends\smallExp640\training\val'
+fromPath = r'O:\Tech_TTH-BITCue\Workspace_Hjalte\candida\3rd sending - photos F. candida tes ends\smallExp1280'
+toPath = r'O:\Tech_TTH-BITCue\Workspace_Hjalte\candida\3rd sending - photos F. candida tes ends\smallExp1280/val'
+
+names = [i for i in os.listdir(namePath)]
+
+
+
+for n in names:
+    src = os.path.join(fromPath, n)
+    dst = os.path.join(toPath, n)
+
+    shutil.move(src, dst)

### 2023-01-27 code/generateTrain.py

@@ -1,0 +1,93 @@
+"""
+Generate candida training data 
+
+For each white/black image
+Pad to 640x640
+Find contours
+Generate bounding boxes
+Output yolo annotations format
+"""
+#from cmath import inf
+#import pandas as pd
+from pyexpat.errors import XML_ERROR_INCOMPLETE_PE
+import cv2
+import matplotlib.pyplot as plt
+import numpy as np
+#import math
+#import imutils
+#import statistics as st
+#import time
+#from scipy.spatial.distance import cdist
+#import matplotlib.animation as animation
+import os
+import shutil
+
+filePath = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\x_20220127'
+
+filesOrig = [i for i in os.listdir(filePath) if i.endswith(".jpg")]
+filesWhite = [i for i in os.listdir(filePath) if i.endswith(".tif")]
+
+print(f'Original files: {filesOrig}')
+print(f'Original files: {filesWhite}')
+
+def generateBB(origName, white):
+    whiteBin = cv2.cvtColor(white, cv2.COLOR_BGR2GRAY)
+    print(whiteBin.shape)
+    whiteBinHeight = whiteBin.shape[0]
+    whiteBinWidth = whiteBin.shape[1]
+    #whiteBin = cv2.imread(os.path.join(filePath, w), cv2.IMREAD_GRAYSCALE) # Read the white/black image
+    _, binary = cv2.threshold(whiteBin, 225, 255, cv2.THRESH_BINARY_INV)
+    cv2.imwrite(os.path.join(filePath, "binaryImages", "binayImage_" + origName + ".jpg"), binary)
+    contours, hierarchy = cv2.findContours(binary, cv2.RETR_EXTERNAL, cv2.CHAIN_APPROX_SIMPLE)[-2:]
+    numContours = 0
+
+    with open(os.path.join(filePath, "data",  origName + ".txt"), 'w') as f:
+        
+        for c in contours:
+            M = cv2.moments(c)
+            x,y,w,h = cv2.boundingRect(c)
+            #print("xywh", x, y, w, h)
+            #print(f'BB coordinates: {x}, {y}, {w}, {h}')
+            # if M['m00'] != 0:
+            #     cx = int(M['m10']/M['m00'])
+            #     cy = int(M['m01']/M['m00'])
+            #     numContours += 1
+            # else:
+            #     cx, cy = 0, 0 #continue # excludes contours without area # To keep:  
[…]

### 2023-01-27 code/main.py

@@ -7,23 +7,31 @@ import numpy as np
 
 ### First look ###
 
-pathImg = r'data\2nd sending - photos F. candida test ends\A34.1\A34.1.jpg' 
+pathImg = r'data\2nd sending - photos F. candida test ends\A34.1\A34.1_ed1.tif' 
 pathDat = r'data\2nd sending - photos F. candida test ends\A34.1\Results_A34.1.csv'
 
+origImg = r'data\2nd sending - photos F. candida test ends\A34.1\A34.1.jpg'
+
 img = cv2.imread(pathImg)
+origImg = cv2.imread(origImg)
+
 dat = pd.read_csv(pathDat, sep=';')
 
 xs = dat['X'].tolist()
-xs = [i * (3000/150) for i in xs] 
+#xs = [i * (3000/255) for i in xs] 
+#xs = [i * (1442/71.25) for i in xs] 
 
 ys = dat['Y'].tolist()
-ys = [i * (3209/150) for i in ys] 
+#ys = [i * (3209/255) for i in ys] 
+#ys = [i * (1767/87.13) for i in ys] 
+
 
 xy = list(zip(xs, ys))
 pts = np.array(xy)
-xs = xs * int(3000/255)
+#xs = xs * int(3000/255)
 
-plt.imshow(img)
+plt.imshow(origImg)
 plt.scatter(pts[:, 0], pts[:, 1], marker="x", color="red", s=2)
 plt.show()
+#plt.savefig("OrigCoord.png")
 

### 2023-01-27 code/pointRefencing.py

@@ -1,0 +1,192 @@
+from cmath import inf
+import pandas as pd
+import cv2
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+import imutils
+import statistics as st
+import time
+from scipy.spatial.distance import cdist
+import matplotlib.animation as animation
+
+pathDat = r'data\2nd sending - photos F. candida test ends\A34.1\Results_A34.1.csv'
+dat = pd.read_csv(pathDat, sep=';')
+
+xs = dat['X'].tolist()
+ys = dat['Y'].tolist()
+xysearch = list(zip(xs, ys))
+ptsSearch = np.array(xysearch)
+
+
+# import cv2
+origImg = r'data\2nd sending - photos F. candida test ends\A34.1\A34.1.jpg' 
+pathImg = r'data\2nd sending - photos F. candida test ends\A34.1\A34.1_ed1.tif' 
+whiteImg = r'data\2nd sending - photos F. candida test ends\A34.1\A34.1_ed2.tif'
+
+orim = cv2.imread(origImg)
+im = cv2.imread(pathImg, cv2.IMREAD_GRAYSCALE)
+imW = cv2.imread(whiteImg)
+
+# Find contours of the b&w image
+_, binary = cv2.threshold(im, 225, 255, cv2.THRESH_BINARY_INV)
+contours, hierarchy = cv2.findContours(binary, cv2.RETR_TREE, cv2.CHAIN_APPROX_SIMPLE)
+
+# Find centroids of the contours
+conx = []
+cony = []
+
+for c in contours:
+    M = cv2.moments(c)
+    x,y,w,h = cv2.boundingRect(c)
+    
+    print(f'BB coordinates: {x}, {y}, {w}, {h}')
+
+    if M['m00'] != 0:
+        cx = int(M['m10']/M['m00'])
+        cy = int(M['m01']/M['m00'])
+        conx.append(cx)
+        cony.append(cy)
+        cv2.drawContours(orim, [c], -1, (0, 255, 0), 2)
+        cv2.rectangle(orim,(x,y),(x+w,y+h),(255,0,0),2)
+        #cv2.circle(orim, (cx, cy), 4, (0, 0, 255), -1)
+        #cv2.putText(im, "center", (cx - 20, cy - 20), cv2.FONT_HERSHEY_SIMPLEX, 0.5, (0, 0, 0), 2)
+    #print(f"x: {cx} y: {cy}")
+
+for c in contours:
+    M = cv2.moments(c)
+
[…]

### 2023-01-27 code/slice2.py

@@ -1,0 +1,129 @@
+import cv2
+import math
+import os
+import pandas as pd
+from shapely.geometry import Polygon
+from PIL import Image
+
+
+split_width = 640
+split_height = 640
+
+
+def start_points(dim, slice_size):
+    ratio = dim/(slice_size)
+    canfit = math.floor(ratio)
+    if canfit == 0: # If dimension can't fit a single slice, use the image as is.
+        return [0]
+    splits = math.ceil(ratio)
+    surplus = (splits-ratio)*(slice_size)
+    surplusPerSlice = surplus/canfit
+
+    print(f'Image dimension: {dim}')
+    print(f'Slice size is {slice_size}. Without overlap slice size is {slice_size}')
+    print("Slices per dimension ", ratio)
+    print(f'We can fit {canfit} slices of size {slice_size}')
+    print(f'We will make {splits} slices')
+    print(f'We have a surplus of {surplus}')
+    print(f"That's {surplusPerSlice} per slice")
+
+    l = []
+    c = 0
+
+    for i in range(splits):
+        l.append(int(((slice_size)-surplusPerSlice)*c))
+        c += 1
+    print("L looks like this: ", l)
+    return l
+
+
+def slice(basename, img, imgDim, anno, xs, ys): 
+    
+    count = 0
+    suffix = 'slice'
+    frmt = 'jpg'
+
+    # we need to rescale coordinates from 0-1 to real image height and width
+    anno[['x1', 'w']] = anno[['x1', 'w']] * imgDim[0]
+    anno[['y1', 'h']] = anno[['y1', 'h']] * imgDim[1]
+    print("Annotations: ")
+    print(anno)
+    print("---")
+    boxes = []
+
+    # convert bounding boxes to shapely polygons. We need to invert Y and find polygon vertices from center points
+    for row in anno.iterrows():
+        x1 = row[1]['x1'] - (row[1]['w']/2)
+        y1 = (imgDim[1] - (row[1]['y1']) - row[1]['h']/2)
+        x2 = row[1]['x1'] + (row[1]['w']/2)
+        y2 = (imgDim[1] - (row[1]['y1']) + row[1]['h']/2)
+        print("Box: ")
+        print(x1, y1, x2, y2)
+        print("---")
+        boxes.append((int(row[1]['class']), Polygon([(x1, y1), (x2, y1), (x2, y2), (x1, y2)])))
+    #print("Main boxes: ", boxes)
+
+    for i in ys:
[…]

### 2023-01-27 code/splitter.py

@@ -1,0 +1,117 @@
+from pulp import LpMaximize, LpMinimize, LpProblem, lpSum, LpVariable, PULP_CBC_CMD, value, LpStatus
+import pandas as pd
+import shutil
+import os
+
+### READ DATA ###
+files = r"O:/Tech_zoo/candida/3rd sending - photos F. candida tes ends/x_20230127/data" # Image and txt files
+data = pd.read_csv(r"O:/Tech_zoo/candida/3rd sending - photos F. candida tes ends/x_20230127/data/statD.txt")
+objects = data['objects'].tolist()
+imageNames = data['image'].tolist()
+
+### CALCULATE SPLITS ###
+def splitObjects(v):
+    """
+    Take 30% of total number of annotations
+    Round to nearest even
+    Split in two -> val, test
+    Remainder is train
+    """
+    
+    def roundEven(num):
+        return round(num / 2) * 2
+
+    valtest = (v/100)*30
+    valtest = roundEven(valtest)
+    val = valtest/2
+    test = val
+    train = v - valtest
+    return [train, int(val), int(test)]
+
+
+perfectImageSplit = splitObjects(len(objects))
+perfectObjectSplit = splitObjects(sum(objects))
+
+groupNames = ["train", "val", "test"]
+print("Perfect image split: ", perfectImageSplit)
+print("Perfect object split: ", perfectObjectSplit)
+
+
+### SET VARIABLES ###
+n_object = len(objects)
+object_keys = range(n_object)
+
+group_sum_targets = perfectObjectSplit
+group_n_objects = perfectImageSplit
+
+n_group = len(group_sum_targets)
+group_keys = range(n_group)
+
+problem_name = 'repex'
+
+### SET UP OPTIMIZATION ###
+# Seek to minimise absolute deviation from the target sums
+prob = LpProblem(problem_name, LpMinimize)
+
+# Primary Decision variables - the assignments
+z = LpVariable.dicts('z',
+                     indices = [(i, j) for i in object_keys for j in group_keys],
+                     cat='Binary')
+
+
+# Aux. decision variables - the sum of groups
+group_sums = LpVariable.dicts('group_sums', indices=group_keys, cat='Continuous')
+group_abs_error = LpVariable.dicts('group_abs_error', indices=group_keys, cat='Continuous')
+
+# Objective - assumes all groups evenly penalised for missing
[…]

### 2023-01-27 code/springtail.py

@@ -1,0 +1,120 @@
+from email.charset import QP
+from PyQt6.QtWidgets import QApplication, QWidget, QPushButton, QLabel, QGridLayout, QMainWindow, QVBoxLayout, QFileDialog
+from PyQt6.QtGui import QIcon, QFont, QAction, QPixmap, QPainter, QColor, QPen, QBrush
+import sys
+from PyQt6.QtCore import Qt, QRect,QPoint
+
+
+class Window(QMainWindow):
+    def __init__(self):
+        super().__init__()
+
+        self.setWindowTitle("Interactive Springtail Counter")
+        self.setWindowIcon(QIcon("icons/flower.png"))
+        self.setGeometry(50, 30, 600, 400)
+
+        self.central_widget = QWidget()               
+        self.setCentralWidget(self.central_widget)    
+        lay = QGridLayout(self.central_widget)
+ 
+        self.label = QLabel(self)
+        self.pixmap = QPixmap('cutout.jpg')
+        self.label.setPixmap(self.pixmap)
+
+
+        self.createMenu()
+        lay.addWidget(self.label)
+        self.show()
+
+  
+
+        # def open_dialog(self):
+        #     fname = QFileDialog.getOpenFileName(
+        #         self,
+        #         "Open File",
+        #         "${HOME}",
+        #         "All Files (*);; Python Files (*.py);; PNG Files (*.png)",
+        #     )
+
+
+        # grid = QGridLayout()
+
+        # btnLoadImg = QPushButton("Load image")
+        # btnDetect = QPushButton("Detect")
+        # btnClose = QPushButton("Exit")
+        # grid.addWidget(btnLoadImg,0,0)
+        # grid.addWidget(btnDetect,1,0)
+        # grid.addWidget(btnClose,0,10)
+
+        # self.setLayout(grid)
+
+    def createMenu(self):
+        mainMenu = self.menuBar()
+        fileMenu = mainMenu.addMenu("File")
+        actionMenu = mainMenu.addMenu("Action")
+
+
+        newAction = QAction(QIcon("icons/image.png"), "Open image...", self)
+        newAction.setShortcut("Ctrl+N")
+        fileMenu.addAction(newAction)
+        self.menu.addAction(self.action)
+        self.action.triggered.connect(self.my_function)
+
+        saveAction = QAction(QIcon("icons/save.png"), "Save...", self)
+        saveAction.setShortcut("Ctrl+S")
[…]

### 2023-01-27 code/temp.py

@@ -1,0 +1,105 @@
+import math
+
+from PyQt6.QtCore import *
+from PyQt6.QtGui import * 
+from PyQt6.QtWidgets import QApplication, QWidget, QPushButton, QGraphicsItem, QGraphicsView, QGraphicsScene, QHBoxLayout,QGraphicsLineItem, QGraphicsPathItem, QVBoxLayout, QGraphicsEllipseItem
+import sys
+
+
+"""
+class Widget(QWidget):
+    def __init__(self, parent=None):
+        QWidget.__init__(self, parent)
+
+        self.btn = QPushButton("Add Line")
+
+        self.gv = QGraphicsView()
+        self.scene = QGraphicsScene(self)
+        self.gv.setScene(self.scene) 
+        #self.gv.setRenderHints(QPainter.Antialiasing | QPainter.SmoothPixmapTransform)
+
+        lay = QHBoxLayout(self)
+        lay.addWidget(self.btn)
+        lay.addWidget(self.gv)
+
+        self.p_item = self.scene.addPixmap(QPixmap("lena.png"))
+        self.btn.clicked.connect(self.add_line)
+
+    def add_line(self):
+        p1 = self.p_item.boundingRect().topLeft()
+        p2 = self.p_item.boundingRect().center()
+        line = QGraphicsLineItem(QLineF(p1, p2), self.p_item)
+        line.setPen(QPen(Qt.GlobalColor.red, 5))
+        line.setFlag(QGraphicsItem.ItemIsMovable, True)
+        line.setFlag(QGraphicsItem.ItemIsSelectable, True)
+        self.gv.fitInView(self.scene.sceneRect())
+
+
+if __name__ == '__main__':
+    app = QApplication(sys.argv)
+    w = Widget()
+    w.show()
+    sys.exit(app.exec())
+"""
+
+
+class Widget(QWidget):
+    def __init__(self, parent=None):
+        QWidget.__init__(self, parent)
+
+        self.btn = QPushButton("Press Me")
+
+        self.gv = QGraphicsView()
+        self.scene = QGraphicsScene(self)
+        self.gv.setScene(self.scene) 
+        #self.gv.setRenderHint(QPainter.Antialiasing | QPainter.SmoothPixmapTransform)
+
+        lay = QVBoxLayout(self)
+        lay.addWidget(self.btn)
+        lay.addWidget(self.gv)
+
+        self.p_item = self.scene.addPixmap(QPixmap("image3.png"))
+        self.p_item.setPos(100, 100)
+
[…]

### 2023-01-27 code/temp2.py

@@ -1,0 +1,72 @@
+import sys
+from PyQt6 import QtCore, QtGui, QtWidgets, uic
+from PyQt6.QtCore import Qt
+
+class MyWidget(QtWidgets.QWidget):
+    def __init__(self):
+        super().__init__()
+        self.setGeometry(30,30,600,400)
+        self.begin = QtCore.QPoint()
+        self.end = QtCore.QPoint()
+        self.show()
+
+    def paintEvent(self, event):
+        qp = QtGui.QPainter(self)
+        br = QtGui.QBrush(QtGui.QColor(300, 50, 50, 400))  
+        qp.setBrush(br)   
+        qp.drawRect(QtCore.QRect(self.begin, self.end))       
+
+    def mousePressEvent(self, event):
+        self.begin = event.pos()
+        self.end = event.pos()
+        self.update()
+
+    def mouseMoveEvent(self, event):
+        self.end = event.pos()
+        self.update()
+
+    # def mouseReleaseEvent(self, event):
+    #     self.begin = event.pos()
+    #     self.end = event.pos()
+    #     self.update()
+
+if __name__ == '__main__':
+    app = QtWidgets.QApplication(sys.argv)
+    window = MyWidget()
+    window.show()
+    app.aboutToQuit.connect(app.deleteLater)
+    sys.exit(app.exec())
+
+"""
+import sys
+from PyQt6.QtWidgets import QApplication, QLabel, QMainWindow
+from PyQt6.QtGui import QPainter, QPixmap
+from PyQt6.QtCore import Qt
+class MainWindow(QMainWindow):
+  def __init__(self):
+    super().__init__()
+    
+    
+    self.label = QLabel()
+    canvas = QPixmap(400, 300)
+    canvas.fill(Qt.GlobalColor.white)
+    self.label.setPixmap(canvas)
+    self.setCentralWidget(self.label)
+    self.draw_something()    
+
+
+  def draw_something(self):
+    pixmap = self.label.pixmap()
+    painter = QPainter()
+    painter.begin(pixmap) 
+    painter.drawLine(10, 10, 300, 200)
+    painter.end()
+
+    self.label.setPixmap(pixmap)
+
+
+app = QApplication(sys.argv)
+window = MainWindow()
+window.show()
+sys.exit(app.exec())
+"""

### 2023-01-27 code/temp3.py

@@ -1,0 +1,60 @@
+from email.charset import QP
+from PyQt6.QtWidgets import QApplication, QWidget, QPushButton, QLabel, QGridLayout, QMainWindow, QVBoxLayout, QLineEdit
+from PyQt6.QtGui import QIcon, QFont, QAction, QPixmap, QPainter, QColor, QPen, QBrush
+import sys
+from PyQt6.QtCore import Qt, QRect,QPoint
+
+
+
+class MainWindow(QMainWindow):
+
+    def __init__(self):
+        super(MainWindow, self).__init__()
+
+        self.setWindowTitle("My App")
+
+        widget = QLabel("Hello")
+        font = widget.font()
+        font.setPointSize(30)
+        widget.setFont(font)
+        widget.setAlignment(Qt.AlignmentFlag.AlignHCenter | Qt.AlignmentFlag.AlignVCenter)
+
+        self.setCentralWidget(widget)
+
+        # widget.setPixmap(QPixmap('cutout.jpg'))
+
+        # widget2 = QLineEdit()
+        # widget2.setMaxLength(10)
+        # widget2.setPlaceholderText("Enter your text")
+
+        # #widget.setReadOnly(True) # uncomment this to make readonly
+
+        # widget2.returnPressed.connect(self.return_pressed)
+        # widget2.selectionChanged.connect(self.selection_changed)
+        # widget2.textChanged.connect(self.text_changed)
+        # widget2.textEdited.connect(self.text_edited)
+
+        # self.setCentralWidget(widget2)
+
+
+    def return_pressed(self):
+        print("Return pressed!")
+        self.centralWidget().setText("BOOM!")
+
+    def selection_changed(self):
+        print("Selection changed")
+        print(self.centralWidget().selectedText())
+
+    def text_changed(self, s):
+        print("Text changed...")
+        print(s)
+
+    def text_edited(self, s):
+        print("Text edited...")
+        print(s)
+
+
+app = QApplication(sys.argv)
+w = MainWindow()
+w.show()
+app.exec()

### 2023-01-27 code/tempCalc.py

@@ -1,0 +1,69 @@
+
+import motmetrics as mm
+import pandas as pd
+import os
+
+# """
+# SAHI outputs predictions in .pickle files. Below we convert these to text files in yolov5 format.
+# """
+
+# pathPickles = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\smallExp1280\results\1280_e705_s256\pickles'
+# pickles = [os.path.join(pathPickles, i) for i in os.listdir(pathPickles)]
+# factor = 1280
+
+# for p in pickles:
+#     pick = pd.read_pickle(p)
+#     print(p)
+#     pb = os.path.splitext(p)[0]
+#     print(pb)
+#     with open(os.path.join(pb + ".txt"), 'w') as f:
+#         for o in pick:
+#             l = vars(vars(o)['bbox'])
+#             print(l)
+
+#             xmin = l['minx']
+#             ymin = l['miny']
+#             xmax = l['maxx']
+#             ymax = l['maxy']
+
+#             c = 0
+#             xc = ((xmin + xmax)/2)/factor
+#             yc = ((ymin + ymax)/2)/factor
+#             w = (xmax - xmin)/factor
+#             h = (ymax - ymin)/factor
+            
+#             f.write(f'{c} {xc} {yc} {w} {h}\n')
+            
+
+########################################
+
+from shapely.geometry import Polygon
+import numpy as np
+import os
+import csv
+
+
+def yolofile_to_lists(path, file):
+    with open(os.path.join(path, file)) as fd:
+            freader = csv.reader(fd, delimiter='\t') 
+            l = []
+            for ld in freader:
+                l.append([float(i) for i in ld[0].split(" ")])
+            print(f'{file}: {len(l)}')
+            return l
+
+
+d = 0 # detections
+
+#pathAnno = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\smallExp1280\training\test'
+pathAnno = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\HjalteTest\anno'
+annotations = [i for i in os.listdir(pathAnno) if i.endswith('.txt')]
+
+for det in annotations:
+    db = os.path.splitext(os.path.basename(det))[0] # Get name without extension
+    listDet = yolofile_to_lists(pathAnno, det)
+    d += len(listDet)
+
+print(d)
+
+

### 2023-01-27 code/visualise.py

@@ -1,0 +1,63 @@
+import cv2, os, csv
+
+factor = 1280
+
+pathImgs = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\HjalteTest\img'
+pathAnno = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\HjalteTest\anno'
+#pathDet = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\smallExp1280\results\1280_e705\runs\detect\1280_e705\labels'
+pathDet = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\HjalteTest\det'
+
+
+imgs = [i for i in os.listdir(pathImgs) if i.endswith(".jpg")]
+annotations = [i for i in os.listdir(pathAnno) if i.endswith(".txt")]
+detections = [i for i in os.listdir(pathDet) if i.endswith(".txt")]
+
+def yolofile_to_lists(path, file):
+    with open(os.path.join(path, file)) as fd:
+            freader = csv.reader(fd, delimiter='\t') 
+            l = []
+            for ld in freader:
+                l.append([float(i) for i in ld[0].split(" ")])
+            return l
+
+
+def yolo_to_poly(box):
+    """
+    #YOLOv5 annotations are xc, yc, w, h (standardized to image dimensions)
+    #This converts to xmin, ymin, xmax, ymax
+
+    """
+    xc, yc, w, h = int(box[1]*factor), int(box[2]*factor), int(box[3]*factor), int(box[4]*factor) # First item in list ignored skipped as this is the object class
+
+    xmin = int(xc-(w/2))
+    ymin = int(yc-(h/2))
+    xmax = int(xc+(w/2))
+    ymax = int(yc+(h/2))
+
+    return [xmin, ymin, xmax, ymax]
+
+
+for i in imgs:
+    print("yep")
+    im = cv2.imread(os.path.join(pathImgs, i))
+    ib = os.path.splitext(os.path.basename(i))[0]
+    
+    for ann in annotations:
+        if ann.startswith(ib):
+            listAnno = yolofile_to_lists(pathAnno, ann)
+    for det in detections:
+        if det.startswith(ib):
+            listDet = yolofile_to_lists(pathDet, det)
+
+
+    for b in listAnno:
+        col = (0, 255, 0)
[…]

### 2023-01-27 code/slice2.py
Rep clean

@@ -33,7 +33,6 @@ def start_points(dim, slice_size):
     for i in range(splits):
         l.append(int(((slice_size)-surplusPerSlice)*c))
         c += 1
-    print("L looks like this: ", l)
     return l
 
 
@@ -46,9 +45,7 @@ def slice(basename, img, imgDim, anno, xs, ys):
     # we need to rescale coordinates from 0-1 to real image height and width
     anno[['x1', 'w']] = anno[['x1', 'w']] * imgDim[0]
     anno[['y1', 'h']] = anno[['y1', 'h']] * imgDim[1]
-    print("Annotations: ")
-    print(anno)
-    print("---")
+
     boxes = []
 
     # convert bounding boxes to shapely polygons. We need to invert Y and find polygon vertices from center points
@@ -57,9 +54,7 @@ def slice(basename, img, imgDim, anno, xs, ys):
         y1 = (imgDim[1] - (row[1]['y1']) - row[1]['h']/2)
         x2 = row[1]['x1'] + (row[1]['w']/2)
         y2 = (imgDim[1] - (row[1]['y1']) + row[1]['h']/2)
-        print("Box: ")
-        print(x1, y1, x2, y2)
-        print("---")
+
         boxes.append((int(row[1]['class']), Polygon([(x1, y1), (x2, y1), (x2, y2), (x1, y2)])))
     #print("Main boxes: ", boxes)
 
@@ -69,15 +64,11 @@ def slice(basename, img, imgDim, anno, xs, ys):
             cv2.imwrite(r'C:\Users\au309263\Desktop\tempCandida\slicedTrain/{}_{}_{}.{}'.format(basename, suffix, count, frmt), split)
             print(f'Image slice _{count}_ written')
             
-
             xmin =  j
             ymin = imgDim[1] - i
             xmax = j + split_width
             ymax = imgDim[1] - i - split_height
-            
-            print("Slice box: ")
-            print(xmin, ymin, xmax, ymax)
-            print("---")
+
             pol = Polygon([(xmin, ymin), (xmax, ymin), (xmax, ymax), (xmin, ymax)])
 
             slice_labels = []
@@ -96,7 +87,7 @@ def slice(basename, img, imgDim, anno, xs, ys):
                     new_width = (max(x) - min(x)) / split_width #imgDim[0] # get bounding box width and height normalized to slice size
                     new_height = (max(y) - min(y)) / split_height #imgDim[1]
                     
[…]

### 2023-01-27 code/slice2.py
Fixed code to deal with images where one or both dimensions are less than slice size

@@ -48,7 +48,7 @@ def slice(basename, img, imgDim, anno, xs, ys):
 
     boxes = []
 
-    # convert bounding boxes to shapely polygons. We need to invert Y and find polygon vertices from center points
+    # convert bounding boxes to shapely polygons. Invert Y and find polygon vertices from center points
     for row in anno.iterrows():
         x1 = row[1]['x1'] - (row[1]['w']/2)
         y1 = (imgDim[1] - (row[1]['y1']) - row[1]['h']/2)
@@ -84,11 +84,11 @@ def slice(basename, img, imgDim, anno, xs, ys):
                     
                     x, y = new_box.exterior.coords.xy # get coordinates of polygon vertices
                     
-                    new_width = (max(x) - min(x)) / split_width #imgDim[0] # get bounding box width and height normalized to slice size
-                    new_height = (max(y) - min(y)) / split_height #imgDim[1]
+                    new_width = (max(x) - min(x)) / split.shape[1] #imgDim[0] # get bounding box width and height normalized to slice size
+                    new_height = (max(y) - min(y)) / split.shape[0] #imgDim[1]
                     
-                    new_x = (centre.coords.xy[0][0] - xmin) / split_width # Normalize central x and invert y for yolo format
-                    new_y = (ymin - centre.coords.xy[1][0]) / split_height
+                    new_x = (centre.coords.xy[0][0] - xmin) / split.shape[1] # Normalize center x and invert y for yolo format
+                    new_y = (ymin - centre.coords.xy[1][0]) / split.shape[0]
 
                     print(f'Old x {centre.coords.xy[0][0]}; New x {new_x}. Xmin was {xmin}.')
                     print(f'Old y {centre.coords.xy[1][0]}; New y {new_y}. Ymin was {ymin}')

### 2023-02-08 code/slice3.py
Solved problem with zero-area BBs and BBs overlapping slice boundaries

@@ -4,20 +4,10 @@ import os
 import pandas as pd
 from shapely.geometry import Polygon
 from PIL import Image
-from math import floor, ceil
+
 
 split_width = 640
 split_height = 640
-
-
-def roundUp(n, d=6):
-    """
-    Round up last decimal of float
-    """
-    d = int('1' + ('0' * d))
-    r = ceil(n * d) / d
-    print(n, "rounded up to ", r)
-    return r
 
 
 def start_points(dim, slice_size):
@@ -71,7 +61,7 @@ def slice(basename, img, imgDim, anno, xs, ys):
     for i in ys:
         for j in xs:
             split = img[i:i+split_height, j:j+split_width]
-            cv2.imwrite(r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\tempCandida\slicedVal/{}_{}_{}.{}'.format(basename, suffix, count, frmt), split)
+            cv2.imwrite(r'C:\Users\au309263\Desktop\tempCandida\debug/slice/{}_{}_{}.{}'.format(basename, suffix, count, frmt), split)
             #print(f'Image slice _{count}_ written')
             
             xmin =  j
@@ -82,7 +72,7 @@ def slice(basename, img, imgDim, anno, xs, ys):
             pol = Polygon([(xmin, ymin), (xmax, ymin), (xmax, ymax), (xmin, ymax)])
 
             slice_labels = []
-            slice_labels_path = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\tempCandida\slicedVal/{}_{}_{}.txt'.format(basename, suffix, count)
+            slice_labels_path = r'C:\Users\au309263\Desktop\tempCandida\debug/slice/{}_{}_{}.txt'.format(basename, suffix, count)
             for box in boxes:
                 if pol.intersects(box[1]):
                     inter = pol.intersection(box[1])        
@@ -105,33 +95,43 @@ def slice(basename, img, imgDim, anno, xs, ys):
                     if (new_width * split.shape[1] < 1) | (new_height * split.shape[0] < 1):
                         continue
                     
-                    d = new_x + (new_width/2) - 1 # If box overlaps right image boundary
+                    d = new_x + (new_width/2) - 1
                     if d > 0:
-                        print("Box overlaps right boundary")
-                        print("x before ", new_x)
-                        new_x = 1 - roundUp(new_width/2)
-                        print("x after ", new_x)
-
-                    d = new_x - (new_width/2) # If box overlaps left image boundary
[…]

### 2023-02-08 text/ManuscriptDraft.Rmd
Edits to manuscript draft

@@
 
-**Detecting small objects and many of them: Using computer vision and deep learning to automate counting of collembola in petri dish samples**
+**Detecting small objects and many of them: Computer vision and deep learning enables high-throughput counting of collembola in petri dish samples**
 
@@
 
+Requires manual counting of
+
+Recent advances in computer vision and deep learning methods enable automation of image analysis including detection of objects of interest.
+
 Here's the abstract.
@@
 # Introduction
+
+Ecotoxiological laboratory studies on soil invertebrates deliver important assessments of compound toxicities.
+
+Manual live counts problematic because of movement of individuals.
+Counting based on images can alleviate this problem.
+Images also allow validation of counts.
 

### 2023-02-22 text/ManuscriptDraft.Rmd
Editions to manuscript

@@
 csl: ./journal-of-ecology.csl
+editor_options: 
+  markdown: 
+    wrap: 72
 ---
@@
 
-**Detecting small objects and many of them: Computer vision and deep learning enables high-throughput counting of collembola in petri dish samples**
+**Detecting small objects and many of them: Computer vision and deep
+learning enables high-throughput counting of collembola in petri dish
+samples**
 
@@
 
-1: Department of Ecoscience, Aarhus University, C.F. Møllers Allé 4-8, 8000 Aarhus C, Denmark\
+1: Department of Ecoscience, Aarhus University, C.F. Møllers Allé 4-8,
+8000 Aarhus C, Denmark\
 
@@
 
-HMRM: 0000-0002-4768-4767, JJSF: 0000-0002-2260-1224, TTH: 0000-0001-5387-3284
+HMRM: 0000-0002-4768-4767, JJSF: 0000-0002-2260-1224, TTH:
+0000-0001-5387-3284
 
@@
 
-Recent advances in computer vision and deep learning methods enable automation of image analysis including detection of objects of interest.
+Recent advances in computer vision and deep learning methods enable
+automation of image analysis including detection of objects of interest.
 
@@
 
-Ecotoxiological laboratory studies on soil invertebrates deliver important assessments of compound toxicities.
+Ecotoxiological laboratory studies on soil invertebrates deliver
+important assessments of compound toxicities.
 
 Manual live counts problematic because of movement of individuals.
-Counting based on images can alleviate this problem.
-Images also allow validation of counts.
+Counting based on images can alleviate this problem. Images also allow
+validation of counts.
 
--Why do we need to count collembola in petri dishes
--What is the problem with the established method
--Developments in computer vision
--How can computer vision help solve our problem
--What are we presenting
+-Why do we need to count collembola in petri dishes -What is the problem
+with the established method -Developments in computer vision -How can
+computer vision help solve our problem -What are we presenting
 
-Counting of collembola in petri dish samples in ecotoxicology experiments requires substantial manual labor by trained technicians.
-The process is time-consuming while the result is a simple census of the present individual collembola.
-Here, we investigated the feasibility of automating collembola counting based on a single image of a sample taken with a handheld camera and a deep learning object detection model.
+Counting of collembola in petri dish samples in ecotoxicology
+experiments requires substantial manual labor by trained technicians.
+The process is time-consuming while the result is a simple census of the
+present individual collembola. Here, we investigated the feasibility of
+automating collembola counting based on a single image of a sample taken
+with a handheld camera and a deep learning object detection model.
 
-Object detection models have gained significant attention for their ability to locate specific objects of interests in images.
-However, reliable detection of very small and very large numbers of objects remains a challenging task.
-In this regard, the present task is particularly challenging owing to the very small size of objects, low distinguishability of animals from background noise, large variation in number of objects in an image, visual variation between samples, and variation in the conditions in which the image was taken, how the image was taken and the camera that was used.
+Object detection models have gained significant attention for their
+ability to locate specific objects of interests in images. However,
+reliable detection of very small and very large numbers of objects
+remains a challenging task. In this regard, the present task is
+particularly challenging owing to the very small size of objects, low
+distinguishability of animals from background noise, large variation in
+number of objects in an image, visual variation between samples, and
+variation in the conditions in which the image was taken, how the image
+was taken and the camera that was used.
 
-In order to ease the manual counting of animals in an image, it is often done by taking an image of the sample and performing the counting in image processing software.
-This allows for marking of counted individual to prevent double-counting and missed individuals and validation of result.
+In order to ease the manual counting of animals in an image, it is often
+done by taking an image of the sample and performing the counting in
+image processing software. This allows for marking of counted individual
+to prevent double-counting and missed individuals and validation of
+result.
 
-One approach has been semi-automated background removal to create a binary blob image ideally containing only animals and all the animals in a dish.
-This has allowed for subsequent automated counting of blobs and thus individuals.
-However, this process still requires substantial manual effort to clean the image and separate individuals to produce reliable results.
+One approach has been semi-automated background removal to create a
+binary blob image ideally containing only animals and all the animals in
+a dish. This has allowed for subsequent automated counting of blobs and
+thus individuals. However, this process still requires substantial
+manual effort to clean the image and separate individuals to produce
+reliable results.
 
-Ideally, counting would be entirely automated with just a single RGB image as input.
+Ideally, counting would be entirely automated with just a single RGB
+image as input.
 
@@
 
-We publish the code together with the trained model to facilitate others to implement automated analysis of ecotoxicology samples.
+We publish the code together with the trained model to facilitate others
+to implement automated analysis of ecotoxicology samples.
 
@@
 -   Overview of method
-o	Standard method
-o	Translating binary to bounding box format for model training
-o	Splitting image/annotation data into training, validation, and testing sets
-o	Slicing images/annotations for full resolution training
-o	Training and testing neural network with sliding window approach
+-   Standard method
+-   Translating binary to bounding box format for model training
+-   Splitting image/annotation data into training, validation, and
+    testing sets
+-   Slicing images/annotations for full resolution training
+-   Training and testing neural network with sliding window approach
 
-The method involved several steps: Translating binary filter images to bounding box format; splitting images into training, validation and testing sets; slicing images and associated annotations to a standard size in order to not loose information from large images because of downscaling; training and testing the neural network with a sliding window approach.
+The method involved several steps: Translating binary filter images to
+bounding box format; splitting images into training, validation and
+testing sets; slicing images and associated annotations to a standard
+size in order to not loose information from large images because of
+downscaling; training and testing the neural network with a sliding
+window approach.
 
@@
 
-Images had substantial variation in size, with the smallest image included being XxX and the largest XxX.
-We sliced to 640 x 640.
-Images were only sliced on dimensions larger than 640, i.e., an image with size 100x1280 would be sliced to two image of 100x640.
+Images had substantial variation in size, with the smallest image
+included being XxX and the largest XxX. We sliced to 640 x 640. Images
+were only sliced on dimensions larger than 640, i.e., an image with size
+100x1280 would be sliced to two image of 100x640.
 
-Training and testing object detection models requires annotated training and testing data.
-Specifically, images containing the objects of interest together with associated annotation data containing coordinates for bounding boxes delimiting the objects are required.
-Here, generation of annotation data was done through automated processing of existing outputs from human analysis.
-The human analysis results in a binary mask output of each petri dish image with black blobs delimiting animals.
-To convert these to bounding boxes, we applied automated contour detection and bounding box creation using Python OpenCV.
-The contour detection produces some errors when there are many objects very close to each other.
-Although the error rate seems low, for this test, images with a very high number of objects were discarded.
-Images from four tests were used (Test A-D).
-Only one image of each sample was used (i.e.
-for A1.1, A1.2, etc., only one image was included).
+Training and testing object detection models requires annotated training
+and testing data. Specifically, images containing the objects of
+interest together with associated annotation data containing coordinates
+for bounding boxes delimiting the objects are required. Here, generation
+of annotation data was done through automated processing of existing
+outputs from human analysis. The human analysis results in a binary mask
+output of each petri dish image with black blobs delimiting animals. To
+convert these to bounding boxes, we applied automated contour detection
+and bounding box creation using Python OpenCV. The contour detection
+produces some errors when there are many objects very close to each
+other. Although the error rate seems low, for this test, images with a
+very high number of objects were discarded. Images from four tests were
+used (Test A-D). Only one image of each sample was used (i.e. for A1.1,
+A1.2, etc., only one image was included).
 
-Contour detection and bounding box derivation was performed for a total of 127 images resulting in a total of 110.553 objects detected and annotated.
-See table x for distribution of images and objects between groups.
+Contour detection and bounding box derivation was performed for a total
+of 127 images resulting in a total of 110.553 objects detected and
+annotated. See table x for distribution of images and objects between
+groups.
 
-Group	Images	Objects
-A	44	66056
-B	39	17479
-C	16	17059
-D	28	9959
+Group Images Objects A 44 66056 B 39 17479 C 16 17059 D 28 9959
 
-To decrease risk of objects not contained in bounding box, we expanded the widths and heights of boxes with 10%.
+To decrease risk of objects not contained in bounding box, we expanded
+the widths and heights of boxes with 10%.
 
@@
 
-The images varied substantially in the number of annotated objects they contained.
-For each experimental group, we split the images into training, validation, and testing at a ratio of 70/15/15 at the level of images while optimizing for a ratio of 70/15/15 at the level of objects.
-If 70% of the images resulted in an unequal remainder or a decimal value, we rounded to a number that would ensure an equal remainder.
-This was done so that we could ensure an equal split between validation and testing in terms of number of images.
-We assigned images to groups by treating the problem as a linear programming problem with the number of images assigned to each group constrained to the 70/15/15 split while the distribution of images to groups were optimized towards lowest deviation from the 70/15/15 split at the level of objects assigned to each group.
+The images varied substantially in the number of annotated objects they
+contained. For each experimental group, we split the images into
+training, validation, and testing at a ratio of 70/15/15 at the level of
+images while optimizing for a ratio of 70/15/15 at the level of objects.
+If 70% of the images resulted in an unequal remainder or a decimal
+value, we rounded to a number that would ensure an equal remainder. This
+was done so that we could ensure an equal split between validation and
+testing in terms of number of images. We assigned images to groups by
+treating the problem as a linear programming problem with the number of
+images assigned to each group constrained to the 70/15/15 split while
+the distribution of images to groups were optimized towards lowest
+deviation from the 70/15/15 split at the level of objects assigned to
+each group.
 
@@
 
-As the suggested method will produce overlap between sliced images when full 640x640 slices cannot be produced, individual animals will sometimes be present in more than one slice.
+As the suggested method will produce overlap between sliced images when
+full 640x640 slices cannot be produced, individual animals will
+sometimes be present in more than one slice.
 
-Slicing produced the following distribution of sliced images and objects:
+Slicing produced the following distribution of sliced images and
+objects:
 
-Set         Images    Objects
-Training    
-Validation    
+Set Images Objects Training\
+Validation\
 Testing
 
-TO DO	# images	# objects
-Train	89	
-Val	19	
-Test	19	
+TO DO \# images \# objects Train 89\
+Val 19\
+Test 19\
 Total 127
@@
 ## Training and testing neural network with sliding window approach
+
 Just do the slice+SAHI approach and compare with standard 640x640.
 
-Deep learning methods
-To test the applicability of object detection models for automatic detection and counting of collembola, we tested two model sizes of the object detection architecture YOLOv5: the small YOLOv5s which takes images with dimensions of 640x640 as input (hereafter referred to as YOLOv5 640), and the YOLOv5s6 which takes images of dimensions 1280x1280 (hereafter referred to as YOLOv5 1280).
-Additionally, we tested the applicability of the Slicing Aided Hyper Inference (SAHI) method for each model.
-This method slices each image during inference in a sliding window manner and performs inference on each slice.
-The method is particularly relevant for detection of small objects.
-Training length was set to 1000 epochs with early stopping with a patience of 100 epochs. Confidence threshold for prediction set to 0.1. Non-maximum suppression IOU threshold set to 0.45.
+Deep learning methods To test the applicability of object detection
+models for automatic detection and counting of collembola, we tested two
+model sizes of the object detection architecture YOLOv5: the small
+YOLOv5s which takes images with dimensions of 640x640 as input
+(hereafter referred to as YOLOv5 640), and the YOLOv5s6 which takes
+images of dimensions 1280x1280 (hereafter referred to as YOLOv5 1280).
+Additionally, we tested the applicability of the Slicing Aided Hyper
+Inference (SAHI) method for each model. This method slices each image
+during inference in a sliding window manner and performs inference on
+each slice. The method is particularly relevant for detection of small
+objects. Training length was set to 1000 epochs with early stopping with
+a patience of 100 epochs. Confidence threshold for prediction set to
+0.1. Non-maximum suppression IOU threshold set to 0.45.
 
-Evaluating detection performance
-Since YOLOv5+SAHI has a different output format than YOLOv5 on its own, customs scripts were created to 1) translate YOLOv5 output pickle files to standard YOLOv5 text files and 2) calculate detection performance variables (precision and recall) for both methods.
-Precision is the number of correct predictions out of all predictions made.
-Recall is the proportion of the true number of objects that were detected by the model.
-F1 is the weighted average of precision and recall.
-A value of 0.3 was used as the IOU threshold for whether bounding boxes overlapped sufficiently to be considered correct.
+Evaluating detection performance Since YOLOv5+SAHI has a different
+output format than YOLOv5 on its own, customs scripts were created to 1)
+translate YOLOv5 output pickle files to standard YOLOv5 text files and
+2) calculate detection performance variables (precision and recall) for
+both methods. Precision is the number of correct predictions out of all
+predictions made. Recall is the proportion of the true number of objects
+that were detected by the model. F1 is the weighted average of precision
+and recall. A value of 0.3 was used as the IOU threshold for whether
+bounding boxes overlapped sufficiently to be considered correct.
+
+## Resolution per petri dish
+
+To investigate the influence of image resolution on detection
+performance, we measured the number of pixels within the limits of the
+petri dish in each image.
 
@@
 
--	Overview of original number of images, lowest resolution, highest resolution, 
--	Translating binary filters to bounding box format
-o	lowest number of annotations, highest number of annotations
--	Splitting images+annotations into training, validation, testing, with linear optimization (at image level but on condition of number of annotations in each set)
--	Slicing images and annotations to avoid downscaling leverage full resolution information
-o	Resulting number of images (mean number of annotations, sd?)
--	Training and testing model
-o	Prediction accuracy
+-   Overview of original number of images, lowest resolution, highest
+    resolution,
+-   Translating binary filters to bounding box format o lowest number of
+    annotations, highest number of annotations
+-   Splitting images+annotations into training, validation, testing,
+    with linear optimization (at image level but on condition of number
+    of annotations in each set)
+-   Slicing images and annotations to avoid downscaling leverage full
+    resolution information o Resulting number of images (mean number of
+    annotations, sd?)
+-   Training and testing model o Prediction accuracy
 
-The model trained on the 640x640 pixel images reached best validation accuracy at epoch 505. The model trained on the 1280x1280 pixel images reached best validation accuracy at epoch 705.
-Table 1 Detection accuracy with the different models.
-Method (IOU 0.3)	Precision	Recall	F1
-YOLOv5 640	0.46	0.19	0.27
-YOLOv5 640 + SAHI (128)	0.60	0.12	0.20
-YOLOv5 1280	0.54	 0.56	0.55
-YOLOv5 1280 + SAHI (128)	0.63	0.41	0.50
+### Standard approach
 
-Table 2 Detection accuracy of YOLOv5 1280 + SAHI with different window sizes for the SAHI slicing (256, 128, 64).
-Model 1280	SAHI 256	SAHI 128	SAHI 64
-IOU 0.3	Precision	Recall	Precision	Recall	Precision	Recall
-	0.57	0.47	0.63	0.41	0.66	0.41
+### Slicing
 
-Fig. 1 Example of image with challenging background. Result from model 640 + SAHI 128. For this image, the precision was 0.16 and the recall 0.83.
+The model trained on the 640x640 pixel images reached best validation
+accuracy at epoch 505. The model trained on the 1280x1280 pixel images
+reached best validation accuracy at epoch 705. Table 1 Detection
+accuracy with the different models. Method (IOU 0.3) Precision Recall F1
+YOLOv5 640 0.46 0.19 0.27 YOLOv5 640 + SAHI (128) 0.60 0.12 0.20 YOLOv5
+1280 0.54 0.56 0.55 YOLOv5 1280 + SAHI (128) 0.63 0.41 0.50
 
-Fig.
-2 Example image from test data set.
-Green bounding boxes are ground truth annotations derived from the binary images.
-Red boxes are detections made by the YOLOV5 1280 model + SAHI.
-In this case, most animals marked in the ground truth are detected by the model (high recall), but the model produces many false positives (low precision).
+Table 2 Detection accuracy of YOLOv5 1280 + SAHI with different window
+sizes for the SAHI slicing (256, 128, 64). Model 1280 SAHI 256 SAHI 128
+SAHI 64 IOU 0.3 Precision Recall Precision Recall Precision Recall 0.57
+0.47 0.63 0.41 0.66 0.41
+
+Fig. 1 Example of image with challenging background. Result from model
+640 + SAHI 128. For this image, the precision was 0.16 and the recall
+0.83.
+
+Fig. 2 Example image from test data set. Green bounding boxes are ground
+truth annotations derived from the binary images. Red boxes are
+detections made by the YOLOV5 1280 model + SAHI. In this case, most
+animals marked in the ground truth are detected by the model (high
+recall), but the model produces many false positives (low precision).
 Note the overlapping detections in one place (middle of image).
 
-Fig. 3 Example outputs from the two different model sizes with and without application of SAHI (128x128 window size). P: precision, r: recall.
+Fig. 3 Example outputs from the two different model sizes with and
+without application of SAHI (128x128 window size). P: precision, r:
+recall.
 
-Table 3 Variation in performance between images (YOLOv5 1280 + SAHI 128).
-Image	Precision	Recall
-A11.1	0.78	1.0
-A17.1	0.54	0.79
-A31.1	0.42	0.71
-A38.1	0.73	0.50
-A49.1	0.10	1.0
-A6.1	0.60	0.78
-B37.1	0.53	0.39
-C3.1	0.48	0.85
-C7.3	0.62	0.68
-D23.1	0.82	0.44
-D4.1	0.20	0.20
-D9.1	0.66	0.09
+Table 3 Variation in performance between images (YOLOv5 1280 + SAHI
+128). Image Precision Recall A11.1 0.78 1.0 A17.1 0.54 0.79 A31.1 0.42
+0.71 A38.1 0.73 0.50 A49.1 0.10 1.0 A6.1 0.60 0.78 B37.1 0.53 0.39 C3.1
+0.48 0.85 C7.3 0.62 0.68 D23.1 0.82 0.44 D4.1 0.20 0.20 D9.1 0.66 0.09
 
@@
 -   What did we present
--	Who can use it – and how
-o	Model ready to test
-o	Code available for training on new data and adaption
--	High resolution images taken in a standardized setting for training and production likely to improve results and should be considered in future studies.
+-   Who can use it -- and how o Model ready to test o Code available for
+    training on new data and adaption
+-   High resolution images taken in a standardized setting for training
+    and production likely to improve results and should be considered in
+    future studies.
 -
 
-The improved precision with increased image dimensions and with the application of SAHI underlines that a main challenge of the task of detecting collembola is the very small object sizes relative to the full image.
+The improved precision with increased image dimensions and with the
+application of SAHI underlines that a main challenge of the task of
+detecting collembola is the very small object sizes relative to the full
+image.
 
-Overlapping detections
-The models tended to produce overlapping detections.
-This will have some influence on the accuracy metrics, but it can be assumed to be minor, since the overlapping detections seems to be rare.
-Overlapping detections are usually removed by non-maximum suppression.
-However, for the present case with very small object, the NMS IOU threshold was likely set too high,
+Overlapping detections The models tended to produce overlapping
+detections. This will have some influence on the accuracy metrics, but
+it can be assumed to be minor, since the overlapping detections seems to
+be rare. Overlapping detections are usually removed by non-maximum
+suppression. However, for the present case with very small object, the
+NMS IOU threshold was likely set too high,
 
-Accuracy of the ground truth annotations
-Considering the similarity between background and animals, there is likely some level of error in the annotations.
-On top of this, the automated extraction of bounding boxes from the binary images could introduce error, e.g.
-when there are many objects close to each other (all though in the present case, such images were discarded).
-If the accuracy of these ground truth annotations is in fact low, it will have detrimental effects on model accuracy.
-To investigate this issue it could be relevant to test the variation in manual annotations between annotators.
+Accuracy of the ground truth annotations Considering the similarity
+between background and animals, there is likely some level of error in
+the annotations. On top of this, the automated extraction of bounding
+boxes from the binary images could introduce error, e.g. when there are
+many objects close to each other (all though in the present case, such
+images were discarded). If the accuracy of these ground truth
+annotations is in fact low, it will have detrimental effects on model
+accuracy. To investigate this issue it could be relevant to test the
+variation in manual annotations between annotators.
 
-Variation in accuracy between test images
-The model accuracy generally varied substantially between images within the test set.
-This is likely because the model has not been trained on a training set of sufficient size and variation, which means the models fails to generalize between images.
+Variation in accuracy between test images The model accuracy generally
+varied substantially between images within the test set. This is likely
+because the model has not been trained on a training set of sufficient
+size and variation, which means the models fails to generalize between
+images.
 
-Different issues with data means that the present experiment was carried out on a limited set of images.
-Issues/challenges with the available data
--	Contour errors when objects are many and close.
--	Test E folder contains no original images (only b/w), so these cannot be used.
--	Many original images without associated b/w image.
--	Several versions of some b/w images. Used latest version in each case.
--	Images have varied dimensions. Standardized by padding as described. This also means variation in size of objects (in pixels).
+Different issues with data means that the present experiment was carried
+out on a limited set of images. Issues/challenges with the available
+data - Contour errors when objects are many and close. - Test E folder
+contains no original images (only b/w), so these cannot be used. - Many
+original images without associated b/w image. - Several versions of some
+b/w images. Used latest version in each case. - Images have varied
+dimensions. Standardized by padding as described. This also means
+variation in size of objects (in pixels).
 
@@
 
-HRMR, JJSF and TTH conceived the idea.
-HMRM conceived and developed the method with contributions from JJSF and TTH.
-HMRM wrote all code.
-HMRM wrote the manuscript with contributions from JJSF and JJSF.
-All authors gave final approval for publication.
+HRMR, JJSF and TTH conceived the idea. HMRM conceived and developed the
+method with contributions from JJSF and TTH. HMRM wrote all code. HMRM
+wrote the manuscript with contributions from JJSF and JJSF. All authors
+gave final approval for publication.
 
@@
 
-The code and data that supports the results in this paper is openly available at <https://github.com/TECOLOGYxyz/springtail>.
+The code and data that supports the results in this paper is openly
+available at <https://github.com/TECOLOGYxyz/springtail>.
 

### 2023-02-22 code/BBsOnImages.py
Slice results

@@ -1,0 +1,67 @@
+import cv2
+import os
+import csv
+
+
+
+
+pathImgs = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\sliced\test'
+pathAnno = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\sliced/test'
+pathDet = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\pickles'
+
+
+imgs = [i for i in os.listdir(pathImgs) if i.endswith(".jpg")]
+annotations = [i for i in os.listdir(pathAnno) if i.endswith(".txt")]
+detections = [i for i in os.listdir(pathDet) if i.endswith(".txt")]
+
+def yolofile_to_lists(path, file):
+    with open(os.path.join(path, file)) as fd:
+            freader = csv.reader(fd, delimiter='\t') 
+            l = []
+            for ld in freader:
+                l.append([float(i) for i in ld[0].split(" ")])
+            return l
+
+
+def yolo_to_poly(box, imgWidth, imgHeight):
+    """
+    #YOLOv5 annotations are xc, yc, w, h (standardized to image dimensions)
+    #This converts to xmin, ymin, xmax, ymax
+
+    """
+    xc, yc, w, h = int(box[1]*imgWidth), int(box[2]*imgHeight), int(box[3]*imgWidth), int(box[4]*imgHeight) # First item in list ignored skipped as this is the object class
+
+    xmin = int(xc-(w/2))
+    ymin = int(yc-(h/2))
+    xmax = int(xc+(w/2))
+    ymax = int(yc+(h/2))
+
+    return [xmin, ymin, xmax, ymax]
+
+
+for i in imgs:
+    print("yep")
+    im = cv2.imread(os.path.join(pathImgs, i))
+    ib = os.path.splitext(os.path.basename(i))[0]
+    
+    imgWidth, imgHeight = im.shape[1], im.shape[0]
+
+    for ann in annotations:
+        if ann.startswith(ib):
+            listAnno = yolofile_to_lists(pathAnno, ann)
+    for det in detections:
+        if det.startswith(ib):
+            listDet = yolofile_to_lists(pathDet, det)
+
+
+    for b in listAnno:
+        col = (0, 255, 0)
[…]

### 2023-02-22 code/analysis.py

@@ -1,13 +1,14 @@
 import motmetrics as mm
 import pandas as pd
 import os
+import cv2
 
 # """
 # SAHI outputs predictions in .pickle files. Below we convert these to text files in yolov5 format.
 # """
 
-# pathPickles = r"C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\debug/pickle"
-# pickles = [os.path.join(pathPickles, i) for i in os.listdir(pathPickles)]
+# pathPickles = r"C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\pickles"
+# pickles = [os.path.join(pathPickles, i) for i in os.listdir(pathPickles) if i.endswith(".pickle")]
 # #factor = 640
 
 # for p in pickles:
@@ -15,6 +16,12 @@ import os
 #     print(p)
 #     pb = os.path.splitext(p)[0]
 #     print(pb)
+
+#     ### GET DIMENSIONS OF IMAGE ###
+#     img = cv2.imread(os.path.join(pb + ".jpg"))
+#     imgHeight, imgWidth = img.shape[0], img.shape[1]
+#     print(imgHeight, imgWidth)
+
 #     with open(os.path.join(pb + ".txt"), 'w') as f:
 #         for o in pick:
 #             l = vars(vars(o)['bbox'])
@@ -26,21 +33,24 @@ import os
 #             ymax = l['maxy']
 
 #             c = 0
-#             xc = ((xmin + xmax)/2)/5967 #/factor
-#             yc = ((ymin + ymax)/2)/7385 #/factor
-#             w = (xmax - xmin)/5967#/factor
-#             h = (ymax - ymin)/7385#/factor
+#             xc = ((xmin + xmax)/2)/imgWidth #/factor
+#             yc = ((ymin + ymax)/2)/imgHeight #/factor
+#             w = (xmax - xmin)/imgWidth #/factor
+#             h = (ymax - ymin)/imgHeight #/factor
             
 #             f.write(f'{c} {xc} {yc} {w} {h}\n')
             
 
-########################################
+#######################################
 
 from shapely.geometry import Polygon
 import numpy as np
 import os
 import csv
 
+
+##### DEFINE SOME VARIABLES #####
+thres = 0.2
 
 
 def yolo_to_poly(box):
@@ -86,6 +96,7 @@ def calculate_iou(box_1, box_2):
 
 def findHits(annotations, detections):
[…]

### 2023-02-22 code/visualise.py

@@ -1,63 +1,103 @@
-import cv2, os, csv
-
-factor = 1280
-
-pathImgs = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\HjalteTest\img'
-pathAnno = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\HjalteTest\anno'
-#pathDet = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\smallExp1280\results\1280_e705\runs\detect\1280_e705\labels'
-pathDet = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\HjalteTest\det'
+import cv2
+import os
+import csv
+import matplotlib.pyplot as plt
+import pandas as pd
 
 
-imgs = [i for i in os.listdir(pathImgs) if i.endswith(".jpg")]
-annotations = [i for i in os.listdir(pathAnno) if i.endswith(".txt")]
-detections = [i for i in os.listdir(pathDet) if i.endswith(".txt")]
+# Load data
+# scores = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\scores.txt'
+# resolutions = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\petripixels\petriPixels.txt'
+# objects = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\objects.txt'
 
-def yolofile_to_lists(path, file):
-    with open(os.path.join(path, file)) as fd:
-            freader = csv.reader(fd, delimiter='\t') 
-            l = []
-            for ld in freader:
-                l.append([float(i) for i in ld[0].split(" ")])
-            return l
+# scores = pd.read_csv(scores)
+# resolutions = pd.read_csv(resolutions)
+# objects = pd.read_csv(objects)
 
+# print(scores)
+# print(resolutions)
+# # Merge
+# x = scores.merge(resolutions, how = 'inner')
+# x = x.merge(objects, how = 'inner')
 
-def yolo_to_poly(box):
-    """
-    #YOLOv5 annotations are xc, yc, w, h (standardized to image dimensions)
-    #This converts to xmin, ymin, xmax, ymax
-
-    """
[…]

### 2023-02-22 text/ManuscriptDraft.Rmd
Editions to manuscript

@@
 
-Evaluating detection performance Since YOLOv5+SAHI has a different
-output format than YOLOv5 on its own, customs scripts were created to 1)
-translate YOLOv5 output pickle files to standard YOLOv5 text files and
-2) calculate detection performance variables (precision and recall) for
-both methods. Precision is the number of correct predictions out of all
-predictions made. Recall is the proportion of the true number of objects
-that were detected by the model. F1 is the weighted average of precision
-and recall. A value of 0.3 was used as the IOU threshold for whether
-bounding boxes overlapped sufficiently to be considered correct.
+Evaluating detection performance
+
+Since YOLOv5+SAHI has a different output format than YOLOv5 on its own,
+customs scripts were created to 1) translate YOLOv5 output pickle files
+to standard YOLOv5 text files and 2) calculate detection performance
+variables (precision and recall) for both methods. Precision is the
+number of correct predictions out of all predictions made. Recall is the
+proportion of the true number of objects that were detected by the
+model. F1 is the weighted average of precision and recall. A value of
+0.3 was used as the IOU threshold for whether bounding boxes overlapped
+sufficiently to be considered correct.
 
@@
 
+The model trained on the standard images reached best validation
+accuracy at epoch xxx.
+
 ### Slicing
 
-The model trained on the 640x640 pixel images reached best validation
-accuracy at epoch 505. The model trained on the 1280x1280 pixel images
-reached best validation accuracy at epoch 705. Table 1 Detection
-accuracy with the different models. Method (IOU 0.3) Precision Recall F1
-YOLOv5 640 0.46 0.19 0.27 YOLOv5 640 + SAHI (128) 0.60 0.12 0.20 YOLOv5
-1280 0.54 0.56 0.55 YOLOv5 1280 + SAHI (128) 0.63 0.41 0.50
+The model trained on the sliced images reached best validation accuracy
+at epoch xxx.
 
-Table 2 Detection accuracy of YOLOv5 1280 + SAHI with different window
-sizes for the SAHI slicing (256, 128, 64). Model 1280 SAHI 256 SAHI 128
-SAHI 64 IOU 0.3 Precision Recall Precision Recall Precision Recall 0.57
-0.47 0.63 0.41 0.66 0.41
+Running inference on image slices with
 
-Fig. 1 Example of image with challenging background. Result from model
-640 + SAHI 128. For this image, the precision was 0.16 and the recall
-0.83.
+Table 1 Detection accuracy with the different models. Method (IOU 0.3)
+Precision Recall F1 YOLOv5 640 0.46 0.19 0.27 YOLOv5 640 + SAHI (128)
+0.60 0.12 0.20 YOLOv5 1280 0.54 0.56 0.55 YOLOv5 1280 + SAHI (128) 0.63
+0.41 0.50
 
@@
 Table 3 Variation in performance between images (YOLOv5 1280 + SAHI
-128). Image Precision Recall A11.1 0.78 1.0 A17.1 0.54 0.79 A31.1 0.42
-0.71 A38.1 0.73 0.50 A49.1 0.10 1.0 A6.1 0.60 0.78 B37.1 0.53 0.39 C3.1
-0.48 0.85 C7.3 0.62 0.68 D23.1 0.82 0.44 D4.1 0.20 0.20 D9.1 0.66 0.09
+128).
+
+Image Precision Recall
 

### 2023-02-27 text/ManuscriptDraft.Rmd
Point about small blob sizes and errors added

@@
 
+The binary masks included blobs with very low areas.
+
+We must assume that small area sizes come with an increased risk of
+error.
+
+We calculated the area of each contour to see if the model accuracy was
+dependent on object area.
+
 ## Splitting data into training, validation, and testing
@@
 
+Importantly, we underline that the error associated with small object
+areas are likely to be human error in the annotation process.
+
 # Acknowledgements

### 2023-02-27 code/generateTrain.py
Producing x_20230227

@@ -22,8 +22,11 @@ import numpy as np
 #import matplotlib.animation as animation
 import os
 import shutil
+import math
 
-filePath = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\x_20230127'
+#filePath = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\x_20230127'
+
+filePath = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\x_20230227'
 
 filesOrig = [i for i in os.listdir(filePath) if i.endswith(".jpg")]
 filesWhite = [i for i in os.listdir(filePath) if i.endswith(".tif")]
@@ -43,72 +46,90 @@ def generateBB(origName, white):
     numContours = 0
 
     with open(os.path.join(filePath, "data",  origName + ".txt"), 'w') as f:
-        
-        for c in contours:
-            M = cv2.moments(c)
-            x,y,w,h = cv2.boundingRect(c)
-            #print("xywh", x, y, w, h)
-            #print(f'BB coordinates: {x}, {y}, {w}, {h}')
-            # if M['m00'] != 0:
-            #     cx = int(M['m10']/M['m00'])
-            #     cy = int(M['m01']/M['m00'])
-            #     numContours += 1
-            # else:
-            #     cx, cy = 0, 0 #continue # excludes contours without area # To keep:  
-             
+        with open(os.path.join(filePath, "area",  origName + "_area" + ".txt"), 'w') as k:
 
-            cv2.drawContours(white, [c], -1, (0, 255, 0), 1)
-            cv2.rectangle(white,(x,y),(x+w,y+h),(255,0,0),1)
-            
-            clas = "0"
-            xYolo = round((x+w/2)/whiteBinWidth, 4)
-            yYolo = round((y+h/2)/whiteBinHeight, 4)
-            wYolo = round(w/whiteBinWidth, 4)
-            hYolo = round(h/whiteBinHeight, 4)
+            for c in contours:
+                M = cv2.moments(c)
+                x,y,w,h = cv2.boundingRect(c)
+                print("M area: ", M['m00'])
+                print("Cnt area: ", cv2.contourArea(c))
 
-            wYolo += wYolo*0.1 # Expand yolo detections with 10%
-            
-            d = xYolo + (wYolo/2) - 1
-            if d > 0:
-                print("d ", d)
-                wYolo -= d
-            
-            d = xYolo - (wYolo/2)
-            if d < 0:
-                print("d ", d)
[…]

### 2023-02-27 code/slice.py

@@ -72,7 +72,7 @@ def slice(basename, img, imgDim, anno, xs, ys):
     for i in ys:
         for j in xs:
             split = img[i:i+split_height, j:j+split_width]
-            cv2.imwrite(r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\tempCandida\slicedTrain/{}_{}_{}.{}'.format(basename, suffix, count, frmt), split)
+            cv2.imwrite(r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\data/slicedTrain/{}_{}_{}.{}'.format(basename, suffix, count, frmt), split)
             #print(f'Image slice _{count}_ written')
             
             xmin =  j
@@ -83,7 +83,7 @@ def slice(basename, img, imgDim, anno, xs, ys):
             pol = Polygon([(xmin, ymin), (xmax, ymin), (xmax, ymax), (xmin, ymax)])
 
             slice_labels = []
-            slice_labels_path = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\tempCandida\slicedTrain/{}_{}_{}.txt'.format(basename, suffix, count)
+            slice_labels_path = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\data/slicedTrain/{}_{}_{}.txt'.format(basename, suffix, count)
             for box in boxes:
                 if pol.intersects(box[1]):
                     inter = pol.intersection(box[1])        
@@ -142,7 +142,7 @@ def slice(basename, img, imgDim, anno, xs, ys):
             count += 1    
 
 
-path = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\tempCandida\train'
+path = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\data\train'
 imgPaths = [os.path.join(path, i) for i in os.listdir(path) if i.endswith('.jpg')]
 
 for image in imgPaths:

### 2023-02-27 code/splitter.py

@@ -4,8 +4,8 @@ import shutil
 import os
 
 ### READ DATA ###
-files = r"O:/Tech_zoo/candida/3rd sending - photos F. candida tes ends/x_20230127/data" # Image and txt files
-data = pd.read_csv(r"O:/Tech_zoo/candida/3rd sending - photos F. candida tes ends/x_20230127/data/statsD.txt")
+files = r"O:/Tech_zoo/candida/3rd sending - photos F. candida tes ends/x_20230227/data" # Image and txt files
+data = pd.read_csv(r"O:/Tech_zoo/candida/3rd sending - photos F. candida tes ends/x_20230227/data/statD.txt")
 objects = data['objects'].tolist()
 imageNames = data['image'].tolist()
 

### 2023-03-13 code/BBsOnImages.py
Code for drawing bounding boxes on images

@@ -3,11 +3,9 @@ import os
 import csv
 
 
-
-
-pathImgs = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\sliced\test'
-pathAnno = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\sliced/test'
-pathDet = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\pickles'
+pathImgs = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\data\test'
+pathAnno = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\data\test'
+pathDet = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\results\sliced\detectSAHI\pickles'
 
 
 imgs = [i for i in os.listdir(pathImgs) if i.endswith(".jpg")]

### 2023-03-13 code/split.py
Rename

@@ -5,7 +5,7 @@ import os
 
 ### READ DATA ###
 files = r"O:/Tech_zoo/candida/3rd sending - photos F. candida tes ends/x_20230227/data" # Image and txt files
-data = pd.read_csv(r"O:/Tech_zoo/candida/3rd sending - photos F. candida tes ends/x_20230227/data/statD.txt")
+data = pd.read_csv(r"O:/Tech_zoo/candida/3rd sending - photos F. candida tes ends/x_20230227/data/statC.txt")
 objects = data['objects'].tolist()
 imageNames = data['image'].tolist()
 
@@ -97,21 +97,21 @@ extractGroups = [eval(str(i)[2:].replace("_", "")) for i in prob.variables() if 
 extractGroups = [[imageNames[i[0]], groupNames[i[1]]] for i in extractGroups]
 print(extractGroups)
 
-### CREATE GROUPS ###
-for g in extractGroups:
-    image = g[0]
-    group = g[1]
-    x = image[0]
+# ### CREATE GROUPS ###
+# for g in extractGroups:
+#     image = g[0]
+#     group = g[1]
+#     x = image[0]
 
-    srcImage = os.path.join(files,x,image+".jpg")
-    srcTxt = os.path.join(files,x,image+".txt")
-    dst = os.path.join(files,group)
-    print(srcImage, " goes to ", dst)
-    print(srcTxt, " goes to ", dst)
+#     srcImage = os.path.join(files,x,image+".jpg")
+#     srcTxt = os.path.join(files,x,image+".txt")
+#     dst = os.path.join(files,group)
+#     print(srcImage, " goes to ", dst)
+#     print(srcTxt, " goes to ", dst)
 
-    if not os.path.exists(dst): # Make directory if it doesn't exist
-        os.makedirs(dst)    
-    shutil.copy(srcImage, dst)
-    shutil.copy(srcTxt, dst)
+#     if not os.path.exists(dst): # Make directory if it doesn't exist
+#         os.makedirs(dst)    
+#     shutil.copy(srcImage, dst)
+#     shutil.copy(srcTxt, dst)
 
-print("All good")
+# print("All good")

### 2023-03-13 code/analyseOriginal.py
Split code for analysing standard model and slicing model

@@ -1,0 +1,175 @@
+
+
+
+import motmetrics as mm
+import pandas as pd
+import os
+import cv2
+
+from shapely.geometry import Polygon
+import numpy as np
+import os
+import csv
+
+from tqdm import tqdm
+
+### Detection Accuracy ###
+
+##### DEFINE SOME VARIABLES #####
+# thres = 0.2
+
+
+# def yolo_to_poly(box):
+#     #YOLOv5 annotations are xc, yc, w, h (standardized to image dimensions)
+#     #Shapely iou calculation takes tl, tr, bl, br.
+
+
+#     #xc, yc, w, h = int(box[1]*factor), int(box[2]*factor), int(box[3]*factor), int(box[4]*factor)
+#     xc, yc, w, h = box[1], box[2], box[3], box[4]
+
+#     tl = [(xc-(w/2)), (yc-(h/2))]
+#     tr = [(xc+(w/2)), (yc-(h/2))]
+#     bl = [(xc-(w/2)), (yc+(h/2))]
+#     br = [(xc+(w/2)), (yc+(h/2))]
+    
+#     # tl = [int(box[1]*factor-(box[3]*factor/2)), int(box[2]*factor-(box[4]*factor/2))]
+#     # tr = [int(box[1]*factor+(box[3]*factor/2)), int(box[2]*factor+(box[4]*factor/2))]
+#     # bl = [int(box[1]*factor-(box[3]*factor/2)), int(box[2]*factor+(box[4]*factor/2))]
+#     # br = [int(box[1]*factor+(box[3]*factor/2)), int(box[2]*factor-(box[4]*factor/2))]
+
+
+#     return [tl, tr, br, bl]
+
+
+# def calculate_iou(box_1, box_2):
+#     """
+#     #[[tl], [tr], [br], [bl]]
+#     #Note: The origin of Coordinate Systems in shapely library is left-bottom where origin in computer graphics is left-top.
+#     #This difference does not affect the IoU calculation, but if you do other types of calculation, this information might be helpful.
+#     """
+
+#     poly_1 = Polygon(box_1)
+#     poly_2 = Polygon(box_2)
+
+#     # print("Box 1 area: ", poly_1.area)
+#     # print("Box 2 area: ", poly_2.area)
+#     # print("Intersection: ", poly_1.intersection(poly_2).area)
+#     # print("Union: ", poly_1.union(poly_2).area)
+
[…]

### 2023-03-13 code/analyseSliced.py

@@ -1,0 +1,189 @@
+import motmetrics as mm
+import pandas as pd
+import os
+import cv2
+
+# """
+# SAHI outputs predictions in .pickle files. Below we convert these to text files in yolov5 format.
+# """
+
+# pathPickles = r"C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\results\sliced\detectSAHI\pickles"
+# pickles = [os.path.join(pathPickles, i) for i in os.listdir(pathPickles) if i.endswith(".pickle")]
+# #factor = 640
+
+# for p in pickles:
+#     pick = pd.read_pickle(p)
+#     print(p)
+#     pb = os.path.splitext(p)[0]
+#     print(pb)
+
+#     ### GET DIMENSIONS OF IMAGE ###
+#     img = cv2.imread(os.path.join(pb + ".jpg"))
+#     imgHeight, imgWidth = img.shape[0], img.shape[1]
+#     print(imgHeight, imgWidth)
+
+#     with open(os.path.join(pb + ".txt"), 'w') as f:
+#         for o in pick:
+#             l = vars(vars(o)['bbox'])
+#             print(l)
+
+#             xmin = l['minx']
+#             ymin = l['miny']
+#             xmax = l['maxx']
+#             ymax = l['maxy']
+
+#             c = 0
+#             xc = ((xmin + xmax)/2)/imgWidth #/factor
+#             yc = ((ymin + ymax)/2)/imgHeight #/factor
+#             w = (xmax - xmin)/imgWidth #/factor
+#             h = (ymax - ymin)/imgHeight #/factor
+            
+#             f.write(f'{c} {xc} {yc} {w} {h}\n')
+            
+
+#######################################
+
+from shapely.geometry import Polygon
+import numpy as np
+import os
+import csv
+
+
+##### DEFINE SOME VARIABLES #####
+thres = 0.2
+
+
+def yolo_to_poly(box):
+    #YOLOv5 annotations are xc, yc, w, h (standardized to image dimensions)
+    #Shapely iou calculation takes tl, tr, bl, br.
+
+
+    #xc, yc, w, h = int(box[1]*factor), int(box[2]*factor), int(box[3]*factor), int(box[4]*factor)
+    xc, yc, w, h = box[1], box[2], box[3], box[4]
+
[…]

### 2023-03-13 text/ManuscriptDraft.Rmd
Addition to text. Knitted and moved to Google Docs for collaboration

--- 2023-02-22 text/ManuscriptDraft.Rmd
@@
 
-Title:
+Alternative titles:
 
@@
 
-#
+**In an imperfect world: Automating collembola counting with deep
+learning in messy data**
 
@@
 
-Hjalte M. R. Mann^1^, James J. Scott-Fordsmand^1^, Toke T. Høye^1^
+Hjalte M. R. Mann^1^, Mónica André, Toke T. Høye^1^ , Jamie Alison,
+James J. Scott-Fordsmand^1^
 
@@
 
-HMRM: 0000-0002-4768-4767, JJSF: 0000-0002-2260-1224, TTH:
-0000-0001-5387-3284
+HMRM: 0000-0002-4768-4767, MA: 0000-0000-0000-0000, JJSF:
+0000-0002-2260-1224, JA: 0000-0000-0000-0000 TTH: 0000-0001-5387-3284
 
@@
 
-Keywords: Collembola, computer vision, deep learning
+Keywords: Collembola, computer vision, deep learning, messy data,
+slicing, linear optimization
 
@@
 
-Requires manual counting of
+Computer vision methods show huge potential.
+
+Real-world data is messy.
+
+Human error is an inevitable fact.
+
+Ground truth is not universal truth.
+
+Ecooxicology risk assessments rely on standardized laboratory processes.
+
+These involve manual counting of collembola in petri dish samples.
 
 Recent advances in computer vision and deep learning methods enable
-automation of image analysis including detection of objects of interest.
-
-Here's the abstract.
+image-based automation of such a task.
 
@@
 
+-   Why do we need to count collembola in petri dishes
+
+-   What is the problem with the established method -Developments in
+    computer vision
+
+-   How cancomputer vision help solve our problem
+
+-   What are we presenting
+
 Ecotoxiological laboratory studies on soil invertebrates deliver
 important assessments of compound toxicities.
-
-Manual live counts problematic because of movement of individuals.
-Counting based on images can alleviate this problem. Images also allow
-validation of counts.
-
--Why do we need to count collembola in petri dishes -What is the problem
-with the established method -Developments in computer vision -How can
-computer vision help solve our problem -What are we presenting
 
@@
 
-Object detection models have gained significant attention for their
-ability to locate specific objects of interests in images. However,
-reliable detection of very small and very large numbers of objects
-remains a challenging task. In this regard, the present task is
-particularly challenging owing to the very small size of objects, low
-distinguishability of animals from background noise, large variation in
-number of objects in an image, visual variation between samples, and
-variation in the conditions in which the image was taken, how the image
-was taken and the camera that was used.
+Manual live counts are problematic because of movement of individuals
+and risk over missing individuals or double-counting. Counting based on
+images can alleviate this problem. Images also allow validation of
+counts.
 
@@
 manual effort to clean the image and separate individuals to produce
-reliable results.
+reliable results. Ideally, counting would be entirely automated with
+just a single RGB image as input. The basis of this work was the output
+of manual processing of images following a standard protocol.
 
-Ideally, counting would be entirely automated with just a single RGB
-image as input.
+Deep learning object detection models have gained significant attention
+for their ability to locate specific objects of interests in images.
+However, reliable detection of very small and very large numbers of
+objects remains a challenging task. In this regard, the present task is
+particularly challenging owing to the very small size of objects, low
+distinguishability of animals from background noise, large variation in
+number of objects in an image, visual variation between samples, and
+variation in the conditions in which the image was taken, how the image
+was taken, and the camera and image resolution that was used.
 
-The basis of this was the output of manual processing of images
+-   Wider implications
+
+    -   Deviations from protocol
+
+    -   Variation in images
+
+    -   Human error
+
+    -   Messy data
 
@@
 -   Overview of method
--   Standard method
 -   Translating binary to bounding box format for model training
@@
     testing sets
+-   Standard method vs slicing method
 -   Slicing images/annotations for full resolution training
--   Training and testing neural network with sliding window approach
+-   Training and testing neural network with standard approach and
+    slicing approach
 
@@
 
+## Raw data
+
+Description of raw data.
+
 ## Generating training and testing data
-
-Images had substantial variation in size, with the smallest image
-included being XxX and the largest XxX. We sliced to 640 x 640. Images
-were only sliced on dimensions larger than 640, i.e., an image with size
-100x1280 would be sliced to two image of 100x640.
 
@@
 
+The binary masks included blobs with very low areas.
+
 ## Splitting data into training, validation, and testing
@@
 
+Splitting images+annotations into training, validation, testing, with
+linear optimization (at image level but on condition of number of
+annotations in each set
+
+| Set        | Images | Objects |
+|------------|--------|---------|
+| Training   | 89     | 77305   |
+| Validation | 19     | 17790   |
+| Testing    | 19     | 15458   |
+
 ## Slicing images and annotations
+
+Images had substantial variation in size, with the smallest image
+included being XxX and the largest XxX. We sliced to 640 x 640. Images
+were only sliced on dimensions larger than 640, i.e., an image with size
+100x1280 would be sliced to two image of 100x640.
 
@@
 
-Set Images Objects Training\
-Validation\
-Testing
-
-TO DO \# images \# objects Train 89\
-Val 19\
-Test 19\
-Total 127
+| Set        | Images | Objects |
+|------------|--------|---------|
+| Train      | 4166   | 93557   |
+| Validation | 849    | 21795   |
+| Test       | 846    | 19127   |
 
@@
 
-Just do the slice+SAHI approach and compare with standard 640x640.
+Standard vs slice+SAHI approach.
 
-Deep learning methods To test the applicability of object detection
-models for automatic detection and counting of collembola, we tested two
-model sizes of the object detection architecture YOLOv5: the small
-YOLOv5s which takes images with dimensions of 640x640 as input
-(hereafter referred to as YOLOv5 640), and the YOLOv5s6 which takes
-images of dimensions 1280x1280 (hereafter referred to as YOLOv5 1280).
-Additionally, we tested the applicability of the Slicing Aided Hyper
-Inference (SAHI) method for each model. This method slices each image
-during inference in a sliding window manner and performs inference on
-each slice. The method is particularly relevant for detection of small
-objects. Training length was set to 1000 epochs with early stopping with
-a patience of 100 epochs. Confidence threshold for prediction set to
-0.1. Non-maximum suppression IOU threshold set to 0.45.
+Standard YOLOv5m (640 x 640 image input)
 
-Evaluating detection performance
+Versus sliced training data and Slicing Aided Hyper Inference (SAHI) at
+inference. This method slices each image during inference in a sliding
+window manner and performs inference on each slice. The method is
+particularly relevant for detection of small objects. Training length
+was set to 2000 epochs with early stopping with a patience of 100
+epochs.
+
+Confidence threshold for prediction:
+
+Non-maximum suppression IOU threshold set to 0.45.
+
+Bounding box evaluation IOU threshold:
+
+## Evaluating detection performance
 
@@
 model. F1 is the weighted average of precision and recall. A value of
-0.3 was used as the IOU threshold for whether bounding boxes overlapped
+0.2 was used as the IOU threshold for whether bounding boxes overlapped
 sufficiently to be considered correct.
@@
 
+# Pixels per object
+
+We calculated the number of pixel of each object to see if the model
+recall was dependent on object area.
+
+We must assume that small area sizes come with an increased risk of
+false negatives but also of human error in the annotation process.
+
 # Results
@@
     resolution,
+
 -   Translating binary filters to bounding box format o lowest number of
     annotations, highest number of annotations
--   Splitting images+annotations into training, validation, testing,
-    with linear optimization (at image level but on condition of number
-    of annotations in each set)
--   Slicing images and annotations to avoid downscaling leverage full
-    resolution information o Resulting number of images (mean number of
-    annotations, sd?)
--   Training and testing model o Prediction accuracy
+
+-   Slicing images and annotations to avoid downscaling and leverage
+    full resolution information
+
+-   Resulting number of images (mean number of annotations, sd?)
+
+-   Training and testing model
+
+-   Prediction accuracy
 
@@
 
-Running inference on image slices with
+Running inference on image slices with SAHI.
 
-Table 1 Detection accuracy with the different models. Method (IOU 0.3)
-Precision Recall F1 YOLOv5 640 0.46 0.19 0.27 YOLOv5 640 + SAHI (128)
-0.60 0.12 0.20 YOLOv5 1280 0.54 0.56 0.55 YOLOv5 1280 + SAHI (128) 0.63
-0.41 0.50
+| Metric    | Standard | Slicing |
+|-----------|----------|---------|
+| Precision | 0.89     | 0.84    |
+| Recall    | 0.09     | 0.90    |
+| F1        |          |         |
 
-Fig. 2 Example image from test data set. Green bounding boxes are ground
-truth annotations derived from the binary images. Red boxes are
-detections made by the YOLOV5 1280 model + SAHI. In this case, most
-animals marked in the ground truth are detected by the model (high
-recall), but the model produces many false positives (low precision).
-Note the overlapping detections in one place (middle of image).
+Conf: 0.1
 
-Fig. 3 Example outputs from the two different model sizes with and
-without application of SAHI (128x128 window size). P: precision, r:
-recall.
-
-Table 3 Variation in performance between images (YOLOv5 1280 + SAHI
-128).
-
-Image Precision Recall
+IOU: 0.2
 
@@
 -   What did we present
--   Who can use it -- and how o Model ready to test o Code available for
-    training on new data and adaption
+-   Who can use it -- and how
+-   Model ready to test
+-   Code available for training on new data and adaption
 -   High resolution images taken in a standardized setting for training
@@
     future studies.
--
 
 The improved precision with increased image dimensions and with the
-application of SAHI underlines that a main challenge of the task of
+slicing approach underline that a main challenge of the task of
 detecting collembola is the very small object sizes relative to the full
@@
 
-Overlapping detections The models tended to produce overlapping
-detections. This will have some influence on the accuracy metrics, but
-it can be assumed to be minor, since the overlapping detections seems to
-be rare. Overlapping detections are usually removed by non-maximum
-suppression. However, for the present case with very small object, the
-NMS IOU threshold was likely set too high,
+Human error. If the accuracy of these ground truth annotations is in
+fact low, it will have detrimental effects on model accuracy.
 
-Accuracy of the ground truth annotations Considering the similarity
-between background and animals, there is likely some level of error in
-the annotations. On top of this, the automated extraction of bounding
-boxes from the binary images could introduce error, e.g. when there are
-many objects close to each other (all though in the present case, such
-images were discarded). If the accuracy of these ground truth
-annotations is in fact low, it will have detrimental effects on model
-accuracy. To investigate this issue it could be relevant to test the
-variation in manual annotations between annotators.
+Variation in accuracy between test images. The overall prediction
+performance was high
 
-Variation in accuracy between test images The model accuracy generally
-varied substantially between images within the test set. This is likely
-because the model has not been trained on a training set of sufficient
-size and variation, which means the models fails to generalize between
-images.
-
-Different issues with data means that the present experiment was carried
-out on a limited set of images. Issues/challenges with the available
-data - Contour errors when objects are many and close. - Test E folder
-contains no original images (only b/w), so these cannot be used. - Many
-original images without associated b/w image. - Several versions of some
-b/w images. Used latest version in each case. - Images have varied
-dimensions. Standardized by padding as described. This also means
-variation in size of objects (in pixels).
+Importantly, we underline that the error associated with small object
+areas can be down to human error in the annotation process.
 

### 2023-03-13 code/slicedHitlist.py
Code for checking if annotations were detected

@@ -1,0 +1,154 @@
+
+
+
+import motmetrics as mm
+import pandas as pd
+import os
+import cv2
+
+from shapely.geometry import Polygon
+import numpy as np
+import os
+import csv
+
+from tqdm import tqdm
+
+### Detection Accuracy ###
+
+##### DEFINE SOME VARIABLES #####
+thres = 0.2
+
+
+def yolo_to_poly(box):
+    #YOLOv5 annotations are xc, yc, w, h (standardized to image dimensions)
+    #Shapely iou calculation takes tl, tr, bl, br.
+
+    xc, yc, w, h = box[1], box[2], box[3], box[4]
+
+    tl = [(xc-(w/2)), (yc-(h/2))]
+    tr = [(xc+(w/2)), (yc-(h/2))]
+    bl = [(xc-(w/2)), (yc+(h/2))]
+    br = [(xc+(w/2)), (yc+(h/2))]
+    
+    return [tl, tr, br, bl]
+
+
+def calculate_iou(box_1, box_2):
+    """
+    #[[tl], [tr], [br], [bl]]
+    #Note: The origin of Coordinate Systems in shapely library is left-bottom where origin in computer graphics is left-top.
+    #This difference does not affect the IoU calculation, but if you do other types of calculation, this information might be helpful.
+    """
+
+    poly_1 = Polygon(box_1)
+    poly_2 = Polygon(box_2)
+
+    iou = poly_1.intersection(poly_2).area / poly_1.union(poly_2).area
+    return iou
+
+def findHits(annotations, detections):
+    em = np.zeros((len(detections), len(annotations)), dtype=float)
+    print(em.shape)
+    for i1, b1 in tqdm(enumerate(detections)):
+        hit = 0
+        b1 = yolo_to_poly(b1)
+        for i2, b2 in enumerate(annotations):
+            b2 = yolo_to_poly(b2)
+            iou = calculate_iou(b1,b2)
+            em[i1,i2] = iou
+
+    # Which annotations have a hit
+    annoHits  = np.where(np.any(em >= thres, axis = 0))
+    annoHits = np.array(annoHits).tolist()[0]
+    print(annoHits)
+
+    hitList = [1 if i in annoHits else 0 for i,k in enumerate(annotations)]
+    print("Hitlist: ", hitList)
+
+    # How many predictions overlap with a ground truth (positives)
+    #p += sum(np.any(em >= thres,axis = 1))
+    # How many predicitons does not overlap with a ground truth (false positives)
[…]

### 2023-03-13 code/visualise.py
Added production of figure showing pixels per object

@@ -3,10 +3,13 @@ import os
 import csv
 import matplotlib.pyplot as plt
 import pandas as pd
+import seaborn as sns
 
 
-# Load data
-# scores = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\scores.txt'
+### ORIGINAL ###
+
+# # #Load data
+# scores = r"C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\results\original\detect\x_20230227Original_scores.txt"
 # resolutions = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\petripixels\petriPixels.txt'
 # objects = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\objects.txt'
 
@@ -14,90 +17,208 @@ import pandas as pd
 # resolutions = pd.read_csv(resolutions)
 # objects = pd.read_csv(objects)
 
-# print(scores)
-# print(resolutions)
 # # Merge
 # x = scores.merge(resolutions, how = 'inner')
 # x = x.merge(objects, how = 'inner')
 
 # x['f1'] = 2*((x['precision']*x['recall'])/(x['precision']+x['recall']))
 
-
 # d = {"A":1,
 #     "B":2,
 #     "C":3,
 #     "D":4}
 
-# group = x['image'].str[:1]
-# group = [d[k] for k in group]
+# groupL = x['image'].str[:1]
+# group = [d[k] for k in groupL]
 
+# x['group'] = groupL
 # x['id'] = group
 # print(x)
 # # Plot
 # #f = plt.figure()    
 # f, axes = plt.subplots(nrows = 3, ncols = 1, sharex=True)
 
-# axes[0].scatter(x['petriPixels'], x['precision'], s = x['objects'], c = x['id'])
-
-
+# axes[0].set_title("Standard")
+# k = axes[0].scatter(x['petriPixels'], x['precision'], s = (x['objects']/9285)*10000, c = x['id'], alpha=0.6, edgecolors="black", label = x['group'])
+# axes[0].set_ylabel("Precision")
+# axes[0].set_ylim(0,1)
 # # for i, txt in enumerate(x['id']):
 # #     axes[0].annotate(x['image'], (x['petriPixels'], x['precision']))
 
[…]

### 2023-03-13 code/generateTrain.py
Script now outputs file with pixel counts

@@ -26,7 +26,7 @@ import math
 
 #filePath = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\x_20230127'
 
-filePath = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\x_20230227'
+filePath = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\raw'
 
 filesOrig = [i for i in os.listdir(filePath) if i.endswith(".jpg")]
 filesWhite = [i for i in os.listdir(filePath) if i.endswith(".tif")]
@@ -36,24 +36,32 @@ print(f'Original files: {filesWhite}')
 
 def generateBB(origName, white):
     whiteBin = cv2.cvtColor(white, cv2.COLOR_BGR2GRAY)
-    print(whiteBin.shape)
+    print("whiteBin shape ", whiteBin.shape)
     whiteBinHeight = whiteBin.shape[0]
     whiteBinWidth = whiteBin.shape[1]
-    #whiteBin = cv2.imread(os.path.join(filePath, w), cv2.IMREAD_GRAYSCALE) # Read the white/black image
     _, binary = cv2.threshold(whiteBin, 225, 255, cv2.THRESH_BINARY_INV)
-    cv2.imwrite(os.path.join(filePath, "binaryImages", "binayImage_" + origName + ".jpg"), binary)
+    #cv2.imwrite(os.path.join(filePath, "binaryImages", "binayImage_" + origName + ".jpg"), binary)
     contours, hierarchy = cv2.findContours(binary, cv2.RETR_EXTERNAL, cv2.CHAIN_APPROX_SIMPLE)[-2:]
     numContours = 0
 
-    with open(os.path.join(filePath, "data",  origName + ".txt"), 'w') as f:
-        with open(os.path.join(filePath, "area",  origName + "_area" + ".txt"), 'w') as k:
-
+    with open(os.path.join(filePath, "data",  "delete"  + origName + ".txt"), 'w') as f:
+        with open(os.path.join(filePath, "pixelCount",  origName + "_pixelCount" + ".txt"), 'w') as k:
+            i = 0
             for c in contours:
+                #print("Cnt area: ", cv2.contourArea(c))
                 M = cv2.moments(c)
                 x,y,w,h = cv2.boundingRect(c)
-                print("M area: ", M['m00'])
-                print("Cnt area: ", cv2.contourArea(c))
[…]

### 2023-03-13 code/copier.py
Swept the floor

@@ -1,16 +1,0 @@
-import shutil
-import os
-
-namePath = r'O:\Tech_TTH-BITCue\Workspace_Hjalte\candida\3rd sending - photos F. candida tes ends\smallExp640\training\val'
-fromPath = r'O:\Tech_TTH-BITCue\Workspace_Hjalte\candida\3rd sending - photos F. candida tes ends\smallExp1280'
-toPath = r'O:\Tech_TTH-BITCue\Workspace_Hjalte\candida\3rd sending - photos F. candida tes ends\smallExp1280/val'
-
-names = [i for i in os.listdir(namePath)]
-
-
-
-for n in names:
-    src = os.path.join(fromPath, n)
-    dst = os.path.join(toPath, n)
-
-    shutil.move(src, dst)

### 2023-03-13 code/main.py

@@ -1,37 +1,0 @@
-
-
-import pandas as pd
-import cv2
-import matplotlib.pyplot as plt
-import numpy as np
-
-### First look ###
-
-pathImg = r'data\2nd sending - photos F. candida test ends\A34.1\A34.1_ed1.tif' 
-pathDat = r'data\2nd sending - photos F. candida test ends\A34.1\Results_A34.1.csv'
-
-origImg = r'data\2nd sending - photos F. candida test ends\A34.1\A34.1.jpg'
-
-img = cv2.imread(pathImg)
-origImg = cv2.imread(origImg)
-
-dat = pd.read_csv(pathDat, sep=';')
-
-xs = dat['X'].tolist()
-#xs = [i * (3000/255) for i in xs] 
-#xs = [i * (1442/71.25) for i in xs] 
-
-ys = dat['Y'].tolist()
-#ys = [i * (3209/255) for i in ys] 
-#ys = [i * (1767/87.13) for i in ys] 
-
-
-xy = list(zip(xs, ys))
-pts = np.array(xy)
-#xs = xs * int(3000/255)
-
-plt.imshow(origImg)
-plt.scatter(pts[:, 0], pts[:, 1], marker="x", color="red", s=2)
-plt.show()
-#plt.savefig("OrigCoord.png")
-

### 2023-03-13 code/pointRefencing.py

@@ -1,192 +1,0 @@
-from cmath import inf
-import pandas as pd
-import cv2
-import matplotlib.pyplot as plt
-import numpy as np
-import math
-import imutils
-import statistics as st
-import time
-from scipy.spatial.distance import cdist
-import matplotlib.animation as animation
-
-pathDat = r'data\2nd sending - photos F. candida test ends\A34.1\Results_A34.1.csv'
-dat = pd.read_csv(pathDat, sep=';')
-
-xs = dat['X'].tolist()
-ys = dat['Y'].tolist()
-xysearch = list(zip(xs, ys))
-ptsSearch = np.array(xysearch)
-
-
-# import cv2
-origImg = r'data\2nd sending - photos F. candida test ends\A34.1\A34.1.jpg' 
-pathImg = r'data\2nd sending - photos F. candida test ends\A34.1\A34.1_ed1.tif' 
-whiteImg = r'data\2nd sending - photos F. candida test ends\A34.1\A34.1_ed2.tif'
-
-orim = cv2.imread(origImg)
-im = cv2.imread(pathImg, cv2.IMREAD_GRAYSCALE)
-imW = cv2.imread(whiteImg)
-
-# Find contours of the b&w image
-_, binary = cv2.threshold(im, 225, 255, cv2.THRESH_BINARY_INV)
-contours, hierarchy = cv2.findContours(binary, cv2.RETR_TREE, cv2.CHAIN_APPROX_SIMPLE)
-
-# Find centroids of the contours
-conx = []
-cony = []
-
-for c in contours:
-    M = cv2.moments(c)
-    x,y,w,h = cv2.boundingRect(c)
-    
-    print(f'BB coordinates: {x}, {y}, {w}, {h}')
-
-    if M['m00'] != 0:
-        cx = int(M['m10']/M['m00'])
-        cy = int(M['m01']/M['m00'])
-        conx.append(cx)
-        cony.append(cy)
-        cv2.drawContours(orim, [c], -1, (0, 255, 0), 2)
-        cv2.rectangle(orim,(x,y),(x+w,y+h),(255,0,0),2)
-        #cv2.circle(orim, (cx, cy), 4, (0, 0, 255), -1)
-        #cv2.putText(im, "center", (cx - 20, cy - 20), cv2.FONT_HERSHEY_SIMPLEX, 0.5, (0, 0, 0), 2)
-    #print(f"x: {cx} y: {cy}")
-
-for c in contours:
-    M = cv2.moments(c)
-
[…]

### 2023-03-13 code/slice.py

@@ -72,7 +72,7 @@ def slice(basename, img, imgDim, anno, xs, ys):
     for i in ys:
         for j in xs:
             split = img[i:i+split_height, j:j+split_width]
-            cv2.imwrite(r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\data/slicedTrain/{}_{}_{}.{}'.format(basename, suffix, count, frmt), split)
+            cv2.imwrite(r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\data/slicedVal/{}_{}_{}.{}'.format(basename, suffix, count, frmt), split)
             #print(f'Image slice _{count}_ written')
             
             xmin =  j
@@ -83,7 +83,7 @@ def slice(basename, img, imgDim, anno, xs, ys):
             pol = Polygon([(xmin, ymin), (xmax, ymin), (xmax, ymax), (xmin, ymax)])
 
             slice_labels = []
-            slice_labels_path = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\data/slicedTrain/{}_{}_{}.txt'.format(basename, suffix, count)
+            slice_labels_path = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\data/slicedVal/{}_{}_{}.txt'.format(basename, suffix, count)
             for box in boxes:
                 if pol.intersects(box[1]):
                     inter = pol.intersection(box[1])        
@@ -142,7 +142,7 @@ def slice(basename, img, imgDim, anno, xs, ys):
             count += 1    
 
 
-path = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\data\train'
+path = r'C:\Users\au309263\OneDrive - Aarhus Universitet\Desktop\candida\data\x_20230227\data\val'
 imgPaths = [os.path.join(path, i) for i in os.listdir(path) if i.endswith('.jpg')]
 
 for image in imgPaths:

### 2023-03-13 code/springtail.py

@@ -1,120 +1,0 @@
-from email.charset import QP
-from PyQt6.QtWidgets import QApplication, QWidget, QPushButton, QLabel, QGridLayout, QMainWindow, QVBoxLayout, QFileDialog
-from PyQt6.QtGui import QIcon, QFont, QAction, QPixmap, QPainter, QColor, QPen, QBrush
-import sys
-from PyQt6.QtCore import Qt, QRect,QPoint
-
-
-class Window(QMainWindow):
-    def __init__(self):
-        super().__init__()
-
-        self.setWindowTitle("Interactive Springtail Counter")
-        self.setWindowIcon(QIcon("icons/flower.png"))
-        self.setGeometry(50, 30, 600, 400)
-
-        self.central_widget = QWidget()               
-        self.setCentralWidget(self.central_widget)    
-        lay = QGridLayout(self.central_widget)
- 
-        self.label = QLabel(self)
-        self.pixmap = QPixmap('cutout.jpg')
-        self.label.setPixmap(self.pixmap)
-
-
-        self.createMenu()
-        lay.addWidget(self.label)
-        self.show()
-
-  
-
-        # def open_dialog(self):
-        #     fname = QFileDialog.getOpenFileName(
-        #         self,
-        #         "Open File",
-        #         "${HOME}",
-        #         "All Files (*);; Python Files (*.py);; PNG Files (*.png)",
-        #     )
-
-
-        # grid = QGridLayout()
-
-        # btnLoadImg = QPushButton("Load image")
-        # btnDetect = QPushButton("Detect")
-        # btnClose = QPushButton("Exit")
-        # grid.addWidget(btnLoadImg,0,0)
-        # grid.addWidget(btnDetect,1,0)
-        # grid.addWidget(btnClose,0,10)
-
-        # self.setLayout(grid)
-
-    def createMenu(self):
-        mainMenu = self.menuBar()
-        fileMenu = mainMenu.addMenu("File")
-        actionMenu = mainMenu.addMenu("Action")
-
-
-        newAction = QAction(QIcon("icons/image.png"), "Open image...", self)
-        newAction.setShortcut("Ctrl+N")
-        fileMenu.addAction(newAction)
-        self.menu.addAction(self.action)
-        self.action.triggered.connect(self.my_function)
-
-        saveAction = QAction(QIcon("icons/save.png"), "Save...", self)
-        saveAction.setShortcut("Ctrl+S")
[…]

### 2023-03-13 code/temp.py

@@ -1,105 +1,0 @@
-import math
-
-from PyQt6.QtCore import *
-from PyQt6.QtGui import * 
-from PyQt6.QtWidgets import QApplication, QWidget, QPushButton, QGraphicsItem, QGraphicsView, QGraphicsScene, QHBoxLayout,QGraphicsLineItem, QGraphicsPathItem, QVBoxLayout, QGraphicsEllipseItem
-import sys
-
-
-"""
-class Widget(QWidget):
-    def __init__(self, parent=None):
-        QWidget.__init__(self, parent)
-
-        self.btn = QPushButton("Add Line")
-
-        self.gv = QGraphicsView()
-        self.scene = QGraphicsScene(self)
-        self.gv.setScene(self.scene) 
-        #self.gv.setRenderHints(QPainter.Antialiasing | QPainter.SmoothPixmapTransform)
-
-        lay = QHBoxLayout(self)
-        lay.addWidget(self.btn)
-        lay.addWidget(self.gv)
-
-        self.p_item = self.scene.addPixmap(QPixmap("lena.png"))
-        self.btn.clicked.connect(self.add_line)
-
-    def add_line(self):
-        p1 = self.p_item.boundingRect().topLeft()
-        p2 = self.p_item.boundingRect().center()
-        line = QGraphicsLineItem(QLineF(p1, p2), self.p_item)
-        line.setPen(QPen(Qt.GlobalColor.red, 5))
-        line.setFlag(QGraphicsItem.ItemIsMovable, True)
-        line.setFlag(QGraphicsItem.ItemIsSelectable, True)
-        self.gv.fitInView(self.scene.sceneRect())
-
-
-if __name__ == '__main__':
-    app = QApplication(sys.argv)
-    w = Widget()
-    w.show()
-    sys.exit(app.exec())
-"""
-
-
-class Widget(QWidget):
-    def __init__(self, parent=None):
-        QWidget.__init__(self, parent)
-
-        self.btn = QPushButton("Press Me")
-
-        self.gv = QGraphicsView()
-        self.scene = QGraphicsScene(self)
-        self.gv.setScene(self.scene) 
-        #self.gv.setRenderHint(QPainter.Antialiasing | QPainter.SmoothPixmapTransform)
-
-        lay = QVBoxLayout(self)
-        lay.addWidget(self.btn)
-        lay.addWidget(self.gv)
-
-        self.p_item = self.scene.addPixmap(QPixmap("image3.png"))
-        self.p_item.setPos(100, 100)
-
[…]

### 2023-03-13 code/temp2.py

@@ -1,72 +1,0 @@
-import sys
-from PyQt6 import QtCore, QtGui, QtWidgets, uic
-from PyQt6.QtCore import Qt
-
-class MyWidget(QtWidgets.QWidget):
-    def __init__(self):
-        super().__init__()
-        self.setGeometry(30,30,600,400)
-        self.begin = QtCore.QPoint()
-        self.end = QtCore.QPoint()
-        self.show()
-
-    def paintEvent(self, event):
-        qp = QtGui.QPainter(self)
-        br = QtGui.QBrush(QtGui.QColor(300, 50, 50, 400))  
-        qp.setBrush(br)   
-        qp.drawRect(QtCore.QRect(self.begin, self.end))       
-
-    def mousePressEvent(self, event):
-        self.begin = event.pos()
-        self.end = event.pos()
-        self.update()
-
-    def mouseMoveEvent(self, event):
-        self.end = event.pos()
-        self.update()
-
-    # def mouseReleaseEvent(self, event):
-    #     self.begin = event.pos()
-    #     self.end = event.pos()
-    #     self.update()
-
-if __name__ == '__main__':
-    app = QtWidgets.QApplication(sys.argv)
-    window = MyWidget()
-    window.show()
-    app.aboutToQuit.connect(app.deleteLater)
-    sys.exit(app.exec())
-
-"""
-import sys
-from PyQt6.QtWidgets import QApplication, QLabel, QMainWindow
-from PyQt6.QtGui import QPainter, QPixmap
-from PyQt6.QtCore import Qt
-class MainWindow(QMainWindow):
-  def __init__(self):
-    super().__init__()
-    
-    
-    self.label = QLabel()
-    canvas = QPixmap(400, 300)
-    canvas.fill(Qt.GlobalColor.white)
-    self.label.setPixmap(canvas)
-    self.setCentralWidget(self.label)
-    self.draw_something()    
-
-
-  def draw_something(self):
-    pixmap = self.label.pixmap()
-    painter = QPainter()
-    painter.begin(pixmap) 
-    painter.drawLine(10, 10, 300, 200)
-    painter.end()
-
-    self.label.setPixmap(pixmap)
-
-
-app = QApplication(sys.argv)
-window = MainWindow()
-window.show()
-sys.exit(app.exec())
-"""

### 2023-03-13 code/temp3.py

@@ -1,60 +1,0 @@
-from email.charset import QP
-from PyQt6.QtWidgets import QApplication, QWidget, QPushButton, QLabel, QGridLayout, QMainWindow, QVBoxLayout, QLineEdit
-from PyQt6.QtGui import QIcon, QFont, QAction, QPixmap, QPainter, QColor, QPen, QBrush
-import sys
-from PyQt6.QtCore import Qt, QRect,QPoint
-
-
-
-class MainWindow(QMainWindow):
-
-    def __init__(self):
-        super(MainWindow, self).__init__()
-
-        self.setWindowTitle("My App")
-
-        widget = QLabel("Hello")
-        font = widget.font()
-        font.setPointSize(30)
-        widget.setFont(font)
-        widget.setAlignment(Qt.AlignmentFlag.AlignHCenter | Qt.AlignmentFlag.AlignVCenter)
-
-        self.setCentralWidget(widget)
-
-        # widget.setPixmap(QPixmap('cutout.jpg'))
-
-        # widget2 = QLineEdit()
-        # widget2.setMaxLength(10)
-        # widget2.setPlaceholderText("Enter your text")
-
-        # #widget.setReadOnly(True) # uncomment this to make readonly
-
-        # widget2.returnPressed.connect(self.return_pressed)
-        # widget2.selectionChanged.connect(self.selection_changed)
-        # widget2.textChanged.connect(self.text_changed)
-        # widget2.textEdited.connect(self.text_edited)
-
-        # self.setCentralWidget(widget2)
-
-
-    def return_pressed(self):
-        print("Return pressed!")
-        self.centralWidget().setText("BOOM!")
-
-    def selection_changed(self):
-        print("Selection changed")
-        print(self.centralWidget().selectedText())
-
-    def text_changed(self, s):
-        print("Text changed...")
-        print(s)
-
-    def text_edited(self, s):
-        print("Text edited...")
-        print(s)
-
-
-app = QApplication(sys.argv)
-w = MainWindow()
-w.show()
-app.exec()

### 2023-03-13 code/tempCalc.py

@@ -1,69 +1,0 @@
-
-import motmetrics as mm
-import pandas as pd
-import os
-
-# """
-# SAHI outputs predictions in .pickle files. Below we convert these to text files in yolov5 format.
-# """
-
-# pathPickles = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\smallExp1280\results\1280_e705_s256\pickles'
-# pickles = [os.path.join(pathPickles, i) for i in os.listdir(pathPickles)]
-# factor = 1280
-
-# for p in pickles:
-#     pick = pd.read_pickle(p)
-#     print(p)
-#     pb = os.path.splitext(p)[0]
-#     print(pb)
-#     with open(os.path.join(pb + ".txt"), 'w') as f:
-#         for o in pick:
-#             l = vars(vars(o)['bbox'])
-#             print(l)
-
-#             xmin = l['minx']
-#             ymin = l['miny']
-#             xmax = l['maxx']
-#             ymax = l['maxy']
-
-#             c = 0
-#             xc = ((xmin + xmax)/2)/factor
-#             yc = ((ymin + ymax)/2)/factor
-#             w = (xmax - xmin)/factor
-#             h = (ymax - ymin)/factor
-            
-#             f.write(f'{c} {xc} {yc} {w} {h}\n')
-            
-
-########################################
-
-from shapely.geometry import Polygon
-import numpy as np
-import os
-import csv
-
-
-def yolofile_to_lists(path, file):
-    with open(os.path.join(path, file)) as fd:
-            freader = csv.reader(fd, delimiter='\t') 
-            l = []
-            for ld in freader:
-                l.append([float(i) for i in ld[0].split(" ")])
-            print(f'{file}: {len(l)}')
-            return l
-
-
-d = 0 # detections
-
-#pathAnno = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\smallExp1280\training\test'
-pathAnno = r'O:\Tech_zoo\candida\3rd sending - photos F. candida tes ends\HjalteTest\anno'
-annotations = [i for i in os.listdir(pathAnno) if i.endswith('.txt')]
-
-for det in annotations:
-    db = os.path.splitext(os.path.basename(det))[0] # Get name without extension
-    listDet = yolofile_to_lists(pathAnno, det)
-    d += len(listDet)
-
-print(d)
-
-
